### 2017-11-15 Paper7.tex
1

\documentclass{article}
\usepackage{verbatim}

\begin{document}
    \input{Chapter2.txt}
\end{document}

### 2017-11-15 render_JYD.sh
Render JYD

@@ -1,0 +1,6 @@
+fileName="Paper7"
+bibPath="~/Documents/Git/BibTex"
+pdflatex $fileName.tex
+bitex $fileName -include-directory=$bibPath
+pdflatex $fileName.tex
+pdflatex $fileName.tex

### 2017-11-15 render_JYD.sh
5

@@ -1,6 +1,7 @@
+#!/bin/bash
 fileName="Paper7"
 bibPath="~/Documents/Git/BibTex"
 pdflatex $fileName.tex
-bitex $fileName -include-directory=$bibPath
+bibtex $fileName -include-directory=$bibPath
 pdflatex $fileName.tex
 pdflatex $fileName.tex

### 2017-11-15 render_JYD.sh
6

@@ -1,7 +1,6 @@
 #!/bin/bash
 fileName="Paper7"
-bibPath="~/Documents/Git/BibTex"
 pdflatex $fileName.tex
-bibtex $fileName -include-directory=$bibPath
+bibtex $fileName
 pdflatex $fileName.tex
 pdflatex $fileName.tex

### 2017-11-30 Body/Abstract.tex
FEUP $(date)

\abstract
The behaviour of concrete-filled steel tubes (CFSTs) is governed by the contribution of both the steel tube and the concrete core, and their interaction may lead to the development of multi-axial stress states, namely the concrete confinement effect and the steel bi-axial stress state. From the previous conducted experimental and numerical study on the behaviour of circular CFST members, it was found that the combination of multi-axial stress states will have a positive effects on the bending capacity of CFST columns. And the multi-axial stress states will cause the underestimation of the analytical results of Distributed Plasticity model. To account for the material strength under multi-axial stress state, strength correction methods, which was developed based on 3D Finite Element (FE) model, had been proposed. This was achieved with a comprehensive parametric study, which considered multiple combinations of steel tube diameter-to-thickness ratios, concrete-to-steel strengths and axial load levels. A section factor ? was used to represent both the geometry and material properties of the CFST members, and ?-dependent correction equations were derived. The feasibility of the equations was verified to be good for both the design and simplified modelling of the CFST members.

### 2017-11-30 Body/Abstract.tex
FEUP $(date)

@@
 \abstract
-The behaviour of concrete-filled steel tubes (CFSTs) is governed by the contribution of both the steel tube and the concrete core, and their interaction may lead to the development of multi-axial stress states, namely the concrete confinement effect and the steel bi-axial stress state.
-From the previous conducted experimental and numerical study on the behaviour of circular CFST members, it was found that the combination of multi-axial stress states will have a positive effects on the bending capacity of CFST columns.
-And the multi-axial stress states will cause the underestimation of the analytical results of Distributed Plasticity model.
-To account for the material strength under multi-axial stress state, strength correction methods, which was developed based on 3D Finite Element (FE) model, had been proposed.
-This was achieved with a comprehensive parametric study, which considered multiple combinations of steel tube diameter-to-thickness ratios, concrete-to-steel strengths and axial load levels.
+The behaviour of concrete-filled steel tubes (CFSTs) is governed by the contribution of both the steel tube and the concrete core.
+Their interaction may lead to the development of multi-axial stress states, namely the concrete confinement effect and the steel bi-axial stress state.
+From the previous conducted experimental and numerical studies on the flexural behaviour of circular CFST members, it was found that the combination of multi-axial stress states will benefit the bending capacity of CFST column.
+Thus, the multi-axial stress states will cause the underestimation on the bending capacity of circular CFST members from the analytical results of Distributed Plasticity (DP) model.
+To account for the material strength under multi-axial stress state and improve the accuracy of the DP model, strength correction methods was developed based on 3D Finite Element (FE) model.
+And with a parametric study, the material strength correction equations to account for the multi-axial stress states had been derived.
 A section factor ?

### 2017-12-01 Body/Section2.tex
FEUP Fri Dec  1 15:29:56 GMTST 2017

\section{Multi-axial Stress States of Circular CFST member}

\subsection{Multi-axial Stress States}

When the CFST members were under loading, composite effects were introduced due to the interaction between concrete core and steel tube. Thus, both the concrete and steel are under multi-axial stress state.

Regarding the concrete, the steel tube will provide confined stress to it and make the material under tri-axial stress state, which is called concrete confinement effect. The strength and the ductility of the concrete is improved by the confinement effect. There were many researchers had studied the concrete confinement effect for CFST members ().

Not only concrete core, but also the steel tube is under multi-axial stress state. The steel tube will provide the confined stress to the concrete core and introduce the confinement effect. In turn, the concrete will expand under axial stress and cause the circumferential stress (or called hoop stress) around the steel tube. As the thickness of the steel tube is relatively small compared to the section diameter, the steel tube could be considered as a 2D shell and the material is under bi-axial stress state (\cite{RN31}). \autoref{fig:steel_biaxial_stress} shows the stress state of the steel tube of circular CFST member. Since the member is under bending force, part of the steel tube is under compression and part of it is under tension. The influences of bi-axial stress state on the steel material properties in the compression and tension areas are different. As can be seen in \autoref{fig:steel_biaxial_stress}, for the compression area, the steel is combined with compressive stress on vertical direction and tensile stress on the horizontal direction. While for the tension area, the steel is under tensile stress at both vertical and horizontal directions.
\begin{figure}[h!]
  \centering
  \includegraphics[width=\linewidth]{Figures/Hoop_Stress.pdf}
  \caption{Steel bi-axial stress state under bending force}
  \label{fig:steel_biaxial_stress}
\end{figure}

To consider the yield stress of steel under bi-axial stress state, the yield surface is introduced (\autoref{fig:von_mises}). It should be noted that, positive value stands for tensile stress whilst negative value presents compressive stress. The hoop stress (\(\sigma_h\)) is plotted at the positive \(x\) axis and the corresponding steel yield stresses under compression (\(f_{yc}\)) and tension (\(f_{yt}\)) are annotated on the yield surface. It could be found that, for steel at compression area, the compressive yield stress is smaller than the uni-axial yield stress (\(f_{y}\)), which will have negative influence on the CFST member capacity. On the contrary, the steel yield stress at tension area will be larger than the uni-axial yield stress, which would benefit the member strength under bending. For circular CFST member under pure compression loading, the whole steel section is under compression and the yield stress of the steel is reduced from (\(f_{y}\)) to (\(f_{yc}\)), Therefore, the steel bi-axial stress has negative influence on the CFST column’s compressive resistance capacity. But for the bending capacity of CFST member, the influence of the steel bi-axial stress state depends on the relative area between the compression part and tension part, since the bi-axial stress state can increase yield stress under tension and reduce yield stress under compression. Thus, if the tensile area of the steel section is larger than the compressive, the steel bi-axial stress will benefit the bending resistance capacity of the CFST members and vice versa.
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.75\linewidth]{Figures/Von_Mises.pdf}
    \caption{Steel yield surface}
    \label{fig:von_mises}
\end{figure}

\subsection{Influence of Multi-axial stress state on Bending Capacity}

As the concrete confinement effect and the steel tensile yield stress can improve the bending capacity while the steel tensile yield stress will decrease the bending capacity of circular specimens. To investigate if the combination of the multi-axial stress states have either positive or negative influence on the bending capacity of circular CFST columns, both experimental and numerical studies had been carried out.

Experimental tests, which were detailed in \cite{Silva2016}, had been conducted to study characterize the bending behaviour of the circular CFST columns under flexural loading. Based on the test results, two numerical models, namely a 3D Finite Element (FE) model and a Distributed Plasticity (DP) model had been proposed to simulate the bending behaviour of circular CFST members. The details of the two numerical models, including the member geometry, the steel-concrete interaction and the material properties, could be found in \cite{Jiang2018}. The 3D model has the possibility to consider the multi-axial stress states of the two materials, since the solid/shell elements were used. While for the DP model, the multi-axial stress state could not be considered as the fibre section could only consider the uni-axial material properties. Thus, the influence of multi-axial stress states on the bending capacity of circular CFST member could be investigated by comparing the predicted results of DP model with the test data.

The lateral load versus drift ratio plots comparison between the experimental and the predicted are plotted in \autoref{fig:test_vs_FE}. It should be noted that, the drift ratio ($\theta$) is defined as the ratio between specimen top lateral displacement and the specimen test length. It could be observed that, the DP model could predict accurate elastic stiffness of CFST members. But regarding the plastic behaviour, the lateral resistances given by the DP model were always lower than the test results. Considering that the DP model could not consider the multi-axial stress state, it could be concluded that, combination of multi-axial stress states could benefit the bending behaviour of the circular CFST member under bending combined with moderate constant axial load. 
\begin{figure}[h!]
    \centering
    \includegraphics[width=\linewidth]{Figures/Test_vs_FE.pdf}
    \caption{Lateral load versus drift ratio plots comparison between test results, 3D FE model and DP model}
    \label{fig:test_vs_FE}
\end{figure}

Regarding the 3D FE model, good agreement is found by comparing its prediction with test results. It proves that, the 3D model could capture the influence of multi-axial load stress state. To further verify the fact, the vertical stress versus vertical strain curves around the steel tube was plotted, as shown in Figure \ref{fig:hoop_stress_FE}. As a reference curve, the uni-axial stress/strain curve of steel model had also been plot in the same figure. The tensile stress/strain was defined as positive value, while the compressive stress/strain were defined as negative value. It could be seen that, the compressive yield stress are less than the uni-axial stress and vice versa, which is in line with the conclusion obtained from the yield surface. Thus, it enhances the fact that, the 3D FE model could capture the multi-axial stress states. 
\begin{figure}[h!]
    \centering
    \includegraphics[width=\linewidth]{Figures/Hoop_Stress_FE.pdf}
    \caption{The vertical stress/strain plots output from the 3D FE model}
    \label{fig:hoop_stress_FE}
\end{figure}

\subsection{Previous Study on Multi-axial Stress State Influence}

In the past, there were many researchers had carried out the studies on prediction of concrete confined stress (Han et al. [2001], Hu et al. [2003], Hu et al. [2005] and Tort and Hajjar [2010]). But in these researches, the influence of steel bi-axial stress state was ignored. Therefore, the derived confined concrete properties by these studies may lead to deviation.

Lai and Varma [2016] had performed parametric study on CFST members under compressive loading with the consideration of multi-axial stress states influences on both concrete and steel. The equation to calculate the confined concrete strength had been derived. Besides that, the steel compressive yield strength was reduced to $0.9f_y$. But regarding the tensile steel yield stress, there was no correction. Thus, the proposed 
 material strength correction equations of Lai and Varma [2016] were suitable for CFST member subjected to axial compression but not for bending.

Fujimoto et al. [2004] and Inai et al. [2004] had used the DP model to predict the bending behaviour of CFST members. To consider the influences of multi-axial stress states, they combined the previous researches on concrete confined stress and steel bi-axial yield stress (Kato and Nishiyama [1980], Sakino and Sun [1994], Nakahara et al. [1999] and Sakino et al. [1998]) and summarized the material strength correction equations for both concrete and steel strength. For circular CFST members, the confined concrete strength was given in Equations (\ref{eq:Sakino_1}) - (\ref{eq:Sakino_2}).
\begin{equation}
    f_{cc} = f_c + 4.1\sigma_r
    \label{eq:Sakino_1}
\end{equation}
\begin{equation}
    \sigma_r = \frac{0.38tf_y}{D - 2t}
    \label{eq:Sakino_2}
\end{equation}

In the studies, a hoop stress of $0.19f_y$ had been assumed and the steel bi-axial yield stress under compression and tension had been adopted as $0.91f_y$ and $1.08f_y$, respectively. To verify the accuracy of the material strength correction equations, the DP models were re-analysed with the corrected material strength. \autoref{tb:sakino} shows the confined concrete strength and the steel bi-axial yield stresses. 
\begin{table}[h!]
  \caption{The corrected material strength for the circular CFST specimens}
  \centering

  \begin{tabular} {*{10}{| c} |}
    \hline
    \multirow{2}{*}{No.}   & \multirow{2}{*}{Specimen Name}    & $D$     & $t$    & $P$    & $f_c$    & $f_y$  & $f_{cc}$    & $f_{yt}$    & $f_{yt}$ \\

        &  & [mm]     & [mm]    & [kN]    & [MPa]    & [MPa]  & [MPa]    & [MPa]    & [MPa] \\
    \hline

    \input{Tables/Table_Sakino.txt}

    \iffalse
    1 & CR-RuC15\%-219-3-0\%-M & 219 & 2.8 & 0 & 20 & 309 & 25 & 281 & 334 \\
    \hline
    2 & CR-RuC15\%-219-3-15\%-M & 219 & 2.8 & 222 & 20 & 309 & 25 & 281 & 334 \\
    \hline
    3 & CR-RuC15\%-219-5-0\%-M & 219 & 4.7 & 0 & 20 & 393 & 32 & 358 & 424 \\
    \hline
    4 & CR-RuC15\%-219-5-15\%-M & 219 & 4.7 & 290 & 20 & 393 & 32 & 358 & 424 \\
    \hline
    5 & CR-RuC5\%-219-5-0\%-M & 219 & 4.7 & 0 & 39 & 393 & 49 & 358 & 424 \\
    \hline
    6 & CR-RuC5\%-219-5-15\%-M & 219 & 4.7 & 359 & 39 & 393 & 49 & 358 & 424 \\
    \hline
    7 & CR-StdC-219-5-0\%-M & 219 & 4.7 & 0 & 53 & 393 & 62 & 358 & 424 \\
    \hline
    8 & CR-StdC-219-5-15\%-M & 219 & 4.7 & 393 & 53 & 393 & 62 & 358 & 424\\
    \fi
    \hline
  \end{tabular}
  \label{tb:sakino}
\end{table}

\autoref{fig:Sakino_verification} displayed the lateral load versus drift ratio curves comparison of three results, namely the tests results, the DP model results with uni-axial material strength and the DP model results with corrected material strength. The 4 plots on the left column belongs to the specimens with no axial load. It could be found that, with the correction methods given by Fujimoto et al. [2004] and Inai et al. [2004], the accuracy of the DP model had been improved, as good agreements were found between corrected DP model and the test results. But regarding the specimens with constant axial loads (plots on the right column), no improvement was found of the corrected DP model compared to the original DP model. As the constant factors were used to corrected the steel bi-axial stress, it could be summarized that the steel bi-axial stress should depends on the axial load level.
\begin{figure}[h!]
    \centering
    \includegraphics[width=\linewidth]{Figures/Sakino_Comparison.pdf}
    \caption{Lateral load versus drift ratio plots comparison between test results, DP model and the corrected DP model}
    \label{fig:Sakino_verification}
\end{figure}

As the aforementioned material strength correction methods were proved to be in-accurate for circular CFST columns under bending combined with constant axial loads, It is necessary to propose new material strength correction methods for both concrete and steel.

### 2017-12-01 Body/Section1.tex
1

Concrete-filled steel tube (CFST) members have been increasingly used in practical design throughout the globe, as it is recognized that such combination of concrete and steel is generally more efficient and economical seismic-resistant solution, in comparison with, for example, reinforced concrete members. The concrete core constrains the steel tube to its interior, thus delaying the occurrence of the local buckling to higher levels of deformation, while the steel tube may allow for the development of confinement effects on the concrete core, thus benefiting both the capacity and ductility of CFSTs.
Regarding the modelling of CFSTs, two numerical modelling approaches have seen widespread use in the scientific community, namely distributed plasticity modelling and 3D finite element modelling. The former is usually combined with fibre elements at multiple sections of the member, (e.g. Aval et al. 2002 [1], Varma et al. 2002 [2], Inai et al. 2004 [3], Han 2004 [4], Liang et al. 2006 [5], Chung 2010 [6], Zubydan and ElSabbagh 2011 [7]), and is commonly validated against experimental data. In order to account for the interaction between the concrete core and the steel tube, advanced fibre element types were derived by different authors, namely modified fibre elements (Valipour and Foster 2010 [8]) and mixed fibre elements (Hajjar et al. 1998 [9], Tort and Hajjar 2009 [10], Tort and Hajjar 2010 [11], Denavit and Hajjar 2011 [12]). However, local buckling effects are not usually captured, and, in some cases, may be critical. As for 3D finite element modelling, it poses the advantage of accounting directly for the interaction between the components of the CFST members, whilst also capturing the development of local buckling effects. However, it is a computationally-heavier approach. Notwithstanding, it has been used to represent the behaviour of CFST members under compression (e.g. Hu et al. 2003 [13], Ellobody et al. 2006 [14], Tao et al. 2013 [15]), bending combined with constant axial load (e.g. Han et al. 2008 [16], Goto et al. 2011 [17], Wang et al. 2014 [18]) and torsion (Han et al. 2007 [19]).
As previously stated, the effect of confinement is one of the key benefits associated with CFST members. On this topic, Hu et al. 2003 [13] carried-out a comprehensive research study on the confinement effect for both circular and rectangular CFST members under compression, deriving closed-form expressions to calculate the confined concrete strength based on the member geometry and material strengths. The paper clearly indicated that these effects are much more substantial for circular members than for rectangular members. The European design code (EN 2004 [20]) follows a similar approach, allowing for the consideration of the confinement effect for design purposes on circular members only. However, the code clearly targets this consideration for members under compression, whilst being very restrictive for bending combined with compression. When it comes to fully flexural loads, the code does not consider any effect of confinement to exist.
As one may have inferred, there is a clear gap in the consideration of multi-axial stress states on CFST members under flexural loads. The research presented in this paper aims to address this limitation of both the literature and the current design methodologies. This paper starts with a brief description of an experimental campaign of CFST columns under monotonic lateral loading combined or not with axial loads. The influence of multi-axial stress states is discussed by comparing the test results with the expected member capacities according to Eurocode 4. In order to have a deep understanding of the multi-axial stress states, two numerical models, namely a 3D finite element model in Abaqus 2014 [21]and a distributed plasticity model in OpenSees (Mazzoni et al. 2006 [22]), were developed and calibrated against experimental data. A strength correction method based on the 3D finite element modelling approach, which aims to overcome the limitations of the distributed plasticity model, was developed and validated. By conducting a parametric study on the flexural behaviour of CFST members, closed-form expressions which focus on the calculation the concrete confinement stress and effective steel strength were derived and their feasibility was verified against experimental data.

### 2017-12-01 Body/Abstract.tex
1

--- 2017-11-30 Body/Abstract.tex
@@
 \abstract
-The behaviour of concrete-filled steel tubes (CFSTs) is governed by the contribution of both the steel tube and the concrete core, and their interaction may lead to the development of multi-axial stress states, namely the concrete confinement effect and the steel bi-axial stress state.
-From the previous conducted experimental and numerical study on the behaviour of circular CFST members, it was found that the combination of multi-axial stress states will have a positive effects on the bending capacity of CFST columns.
-And the multi-axial stress states will cause the underestimation of the analytical results of Distributed Plasticity model.
-To account for the material strength under multi-axial stress state, strength correction methods, which was developed based on 3D Finite Element (FE) model, had been proposed.
-This was achieved with a comprehensive parametric study, which considered multiple combinations of steel tube diameter-to-thickness ratios, concrete-to-steel strengths and axial load levels.
-A section factor ?
-was used to represent both the geometry and material properties of the CFST members, and ?-dependent correction equations were derived.
-The feasibility of the equations was verified to be good for both the design and simplified modelling of the CFST members.
+The behaviour of concrete-filled steel tubes (CFSTs) is governed by the contribution of the steel tube and the concrete core.
+Their interaction will lead to the development of multi-axial stress states, namely the concrete confinement effect and the steel bi-axial stress state.
+From the previous experimental and numerical studies on the flexural behaviour of circular CFST members, the combination of multi-axial stress states was found to benefit the bending capacity of CFST columns.
+Therefore, the bending capacity of the CFST columns will be underestimated when the Distributed Plasticity (DP) model with uni-axial material properties are used.
+To account for the material strength under multi-axial stress state and improve the accuracy of DP model, strength correction methods were proposed based on the analytical results of 3D Finite Element (FE) model.
+Based on the material strength correction methods, a comprehensive parametric study, which involved a large range of CFST cross-section Diameter-thickness ratios, material properties and axial load levels, had been carried out.
+A section factor $\xi$ was used to represent both the geometry and material properties of CFST cross-section.
+According to the parametric study, the confined concrete strength under bending was found to be independent on the constant axial load level.
+On the contrary, the steel bi-axial stress was proved to be sensitive on the constant axial load level.
+With statistic operations, $\xi$-dependent correction equations were derived to account for the material strength variation under multi-axial stress states.
+The feasibility of the material strength correction equations was verified to be good for both the design and the modelling of circular CFST members.

### 2017-12-01 Body/Section1.tex
rasp

@@
-Concrete-filled steel tube (CFST) members have been increasingly used in practical design throughout the globe, as it is recognized that such combination of concrete and steel is generally more efficient and economical seismic-resistant solution, in comparison with, for example, reinforced concrete members.
-The concrete core constrains the steel tube to its interior, thus delaying the occurrence of the local buckling to higher levels of deformation, while the steel tube may allow for the development of confinement effects on the concrete core, thus benefiting both the capacity and ductility of CFSTs.
+Concrete-filled steel tube (CFST) members have been increasingly used in practical design throughout the globe, as it is recognized that such combination of concrete and steel is generally more efficient and economical seismic-resistant solution, in comparison with, for example, reinforced concrete members (Morino).
+The concrete core constrains the steel tube to its interior, thus delaying the occurrence of the local buckling to higher levels of deformation and the ductility of the steel tube is improved.
+Besides the ductility, the composition of concrete and steel will also cause both of the two components under multi-axial stress state and thus, leads to the material properties change.
+Regarding the concrete core, the steel tube provides the confined stress to it and make it under tri-axial stress state.
+The strength and ductility of concrete are enhanced by the confinement effects.
+
 Regarding the modelling of CFSTs, two numerical modelling approaches have seen widespread use in the scientific community, namely distributed plasticity modelling and 3D finite element modelling.
@@
 2007 [19]).
+
 As previously stated, the effect of confinement is one of the key benefits associated with CFST members.
@@
 When it comes to fully flexural loads, the code does not consider any effect of confinement to exist.
+
 As one may have inferred, there is a clear gap in the consideration of multi-axial stress states on CFST members under flexural loads.

### 2017-12-01 Body/Section1.tex
rasp

@@
-Concrete-filled steel tube (CFST) members have been increasingly used in practical design throughout the globe, as it is recognized that such combination of concrete and steel is generally more efficient and economical seismic-resistant solution, in comparison with, for example, reinforced concrete members (Morino).
+Concrete-filled steel tube (CFST) members have been increasingly used in practical design throughout the globe, as it is recognized that such combination of concrete and steel is generally more efficient and economical seismic-resistant solution, in comparison with, for example, reinforced concrete members (Morino et al.
+2001).
 The concrete core constrains the steel tube to its interior, thus delaying the occurrence of the local buckling to higher levels of deformation and the ductility of the steel tube is improved.
 Besides the ductility, the composition of concrete and steel will also cause both of the two components under multi-axial stress state and thus, leads to the material properties change.
-Regarding the concrete core, the steel tube provides the confined stress to it and make it under tri-axial stress state.
-The strength and ductility of concrete are enhanced by the confinement effects.
+Regarding the concrete core, the steel tube provides the confined stress to it and make it under tri-axial stress state, which is well known as concrete confinement effect.
+The strength and ductility of the concrete core are enhanced by the confinement effect, which will benefits the capacity of CFST member under either compression or bending.
+In recent years, there were many researchers had investigated the concrete confinement effect of CFST members.
+Based on the test results, Sakino et al.
+2004 pointed out that, there was confinement effect existing in CFST members under compressive loading, and the circular CFST members should be a more significant concrete confinement effect than the rectangular columns.
+Similarly, Fujimoto et al.
+2004 and Inai et al.
+2004 had performed the experimental tests on the behaviour of CFST members under eccentric compressive loading and bending, respectively.
+And the researchers found that the concrete confinement effect could be neglected for rectangular CFST columns.
 
-Regarding the modelling of CFSTs, two numerical modelling approaches have seen widespread use in the scientific community, namely distributed plasticity modelling and 3D finite element modelling.
-The former is usually combined with fibre elements at multiple sections of the member, (e.g.
-Aval et al.
-2002 [1], Varma et al.
-2002 [2], Inai et al.
-2004 [3], Han 2004 [4], Liang et al.
-2006 [5], Chung 2010 [6], Zubydan and ElSabbagh 2011 [7]), and is commonly validated against experimental data.
-In order to account for the interaction between the concrete core and the steel tube, advanced fibre element types were derived by different authors, namely modified fibre elements (Valipour and Foster 2010 [8]) and mixed fibre elements (Hajjar et al.
-1998 [9], Tort and Hajjar 2009 [10], Tort and Hajjar 2010 [11], Denavit and Hajjar 2011 [12]).
-However, local buckling effects are not usually captured, and, in some cases, may be critical.
-As for 3D finite element modelling, it poses the advantage of accounting directly for the interaction between the components of the CFST members, whilst also capturing the development of local buckling effects.
-However, it is a computationally-heavier approach.
-Notwithstanding, it has been used to represent the behaviour of CFST members under compression (e.g.
-Hu et al.
-2003 [13], Ellobody et al.
-2006 [14], Tao et al.
-2013 [15]), bending combined with constant axial load (e.g.
-Han et al.
-2008 [16], Goto et al.
-2011 [17], Wang et al.
-2014 [18]) and torsion (Han et al.
-2007 [19]).
+The steel tube of CFST member will also be under multi-axial stress states under loading, which is caused by the expansion of concrete core.
+The multi-axial stress states will make the steel have different yield stress under compression and tension.
+In the research works of Fujimoto et al.
+2004, Inai et al.
+2004 and Varmar and Lai 2016, a reduction of steel yield stress had been made when consider the capacity of CFST under compression.
+While for the tensile yield stress of steel, Fujimoto et al.
+2004 and Inai et al.
+2004 considered that the multi-axial stress states would have a positive influence on the tensile yield stress of the steel, and thus, an amplification on it was made.
+To accurately predict the behaviour of CFST member, the multi-axial stress states should be considered during the modelling.
+The 3D Finite Element (FE) model was a commonly used numerical model by many researchers (Hu et al.
+2003, Ellobody et al.
+2006, Wang et al.
+2014, Varma and Lai 2016 etc.).
+Since the 3D FE model used 3D/2D elements, it could consider the material strength change under complex axial stress states.
+Therefore, the model was proved to be accurate in simulating the response of CFST members under different loading types, namely under axial load (Hu et al.
+2003, Ellobody et al.
+2005 and Duarte et al.
+2016), under monotonic bending (Hu et al.
+2005,nad Wang et al.
+2014) and under cyclic bending (Goto et al.
+2010and Imano et al.
+2015).
 
-As previously stated, the effect of confinement is one of the key benefits associated with CFST members.
-On this topic, Hu et al.
-2003 [13] carried-out a comprehensive research study on the confinement effect for both circular and rectangular CFST members under compression, deriving closed-form expressions to calculate the confined concrete strength based on the member geometry and material strengths.
-The paper clearly indicated that these effects are much more substantial for circular members than for rectangular members.
-The European design code (EN 2004 [20]) follows a similar approach, allowing for the consideration of the confinement effect for design purposes on circular members only.
-However, the code clearly targets this consideration for members under compression, whilst being very restrictive for bending combined with compression.
-When it comes to fully flexural loads, the code does not consider any effect of confinement to exist.
+Besides the 3D FE model, the Distributed Plasticity (DP) model was also a common choice of modelling CFST columns (Aval et al.
+2002, Han et al.
+2004, Chung 2010, Zubydan and ElSabbagh 2011 etc.).
+As the DP model is a simplified numerical solution with fibre element represented as the CFST cross-section, it could not capture the multi-axial stress states, namely the concrete confinement effect and the steel bi-axial stress states.
+Therefore, the material properties should be corrected when applicating the DP model.
+Nearly all the researchers (Han et al.
+2004, Valipour and Foster 2010, Zubydan and ElSabbagh 2011, Tort and Hajjar 2010, Liang et al.
+2006) had considered the concrete confinement effects during the modelling, but regarding the steel bi-axial stress.The neglecting of steel bi-axial stress states of CFST member during the behaviour study of CFST member may miss leading the analytical results and decrease the accuracy of the DP model.
+On the contray, Fujimoto et al.
+2004, Inai et al.
+2004 and Varma and Lai 2016 had considered both concrete confinement effect and the steel bi-axial stress states, the feasibility of these methods are detailed in Section 2.
 
-As one may have inferred, there is a clear gap in the consideration of multi-axial stress states on CFST members under flexural loads.
+Regarding the Eurocode 4 design provision, the multi-axial stress states of circular CFST member was considered during the calculation of its plastic resistance capacity under axial compression.
+The confined concrete strength and the corrected steel yield stress are considered in the code.
+However, the code clearly targets this consideration for member under compression, whilst being very restrictive for bending combined with compression.
+When it comes to fully flexural loads, the codes does not consider any effect of confinement to exist.
+As one may have inferred, there is a clear gap in the consideration of multi-axial stress states, including both concrete confinement effect and steel bi-axial stress state, on CFST members under flexural loads.
 The research presented in this paper aims to address this limitation of both the literature and the current design methodologies.
-This paper starts with a brief description of an experimental campaign of CFST columns under monotonic lateral loading combined or not with axial loads.
-The influence of multi-axial stress states is discussed by comparing the test results with the expected member capacities according to Eurocode 4.
-In order to have a deep understanding of the multi-axial stress states, two numerical models, namely a 3D finite element model in Abaqus 2014 [21]and a distributed plasticity model in OpenSees (Mazzoni et al.
-2006 [22]), were developed and calibrated against experimental data.
-A strength correction method based on the 3D finite element modelling approach, which aims to overcome the limitations of the distributed plasticity model, was developed and validated.
+This paper starts with a brief description of the multi-axial stress states and the verification of previous proposed material strength correction methods.
+A strength correction method based on the 3D FE modelling approach, which aims to overcome the limitations of the DP model, was developed and validated.
 By conducting a parametric study on the flexural behaviour of CFST members, closed-form expressions which focus on the calculation the concrete confinement stress and effective steel strength were derived and their feasibility was verified against experimental data.

### 2018-03-26 render_JYD.sh
$(data)

@@ -1,6 +1,0 @@
-#!/bin/bash
-fileName="Paper7"
-pdflatex $fileName.tex
-bibtex $fileName
-pdflatex $fileName.tex
-pdflatex $fileName.tex

### 2018-03-26 Paper7.tex
2
4
5
6
1
FEUP
FEUP $(date)
$(data)

@@
-\documentclass{article}
-\usepackage{verbatim}
+\documentclass[12pt, A4]{article}
+\usepackage{geometry}
+\geometry{margin=1in}
+
+\title{Influence of Multi-Axial Stress States on the Flexural Behaviour of Circular Concrete-Filled Steel Tubes}
+\author{Yadong Jiang \and António Silva \and Bledar Kalemia \and José Miguel Castro \and Ricardo Monteiro}
+
+\date{}
 
 \begin{document}
-    \input{Chapter2.txt}
+	\maketitle
+
+	\begin{abstract}
+		The paper proposes the methodologies and the equations to consider the influence of multi-axial stress states on material strength of circular Concrete-filled Steel Tubular (CFST) columns.
+From the previous experimental and numerical studies on the flexural behaviour of circular CFST members, the combination of multi-axial stress states, namely the concrete confinement effects and the steel bi-axial stress states, was found to benefit the bending capacity of CFST columns.
+Therefore, the bending capacity of the CFST columns will be underestimated by the Distributed Plasticity (DP) model when uni-axial material properties are used.
+To account for the material strength variation under multi-axial stress states and to improve the accuracy of the DP model, material strength correction methods were proposed based on the analytical results given by the 3D Finite Element (FE) model.
+A comprehensive parametric study, which involved a wide range of diameter-thickness ratios, material properties and axial load levels, had been carried out to study the influence of CFST cross-section properties on the multi-axial stress states.
+Based on the parametric study, the confined concrete strength under bending was found to be independent on the constant axial load level.
+On the contrary, the steel bi-axial stress was proved to be sensitive to the constant axial load level.
+A section factor $\xi$ was used to represent both the geometry and material properties of a CFST cross-section.
+With statistic operations, $\xi$-dependent correction equations were derived to account for the material strength variation under multi-axial stress states.
+The feasibility of the proposed material strength correction equations was verified to be good for both the design and modelling of circular CFST members.
+	\end{abstract}
+
+	\section{Introduction}
+	The behaviour of concrete-filled steel tubes (CFSTs) is governed by the contribution of the steel tube and the concrete core.
+As concluded from previous experimental studies (\cite{})The concrete core constrains the steel tube to its interior, thus delaying the occurrence of the local buckling to higher levels of deformation and the ductility of the steel tube is improved.
+Besides its excellent ductility, the composition of concrete and steel will also cause the two components under multi-axial stress state and thus, lead to the material properties change.
+The steel tube provides the confined stress to the concrete core and make it under tri-axial stress state, which is well known as concrete confinement effect.
+The strength and ductility of the concrete core are enhanced by the confinement effect, therefore, the capacity of CFST member under either compression or bending is benefited.
+In recent years, there were many researchers had investigated the concrete confinement effect of CFST members.
+Based on the test results, Sakino et al.
+2004 [2], Fujimoto et al.
+2004 [3] and Inai et al.
+2004 [4] had tested circular and rectangular CFST columns under axial compressive loading, eccentric compressive loading and bending, respectively.
+All the researchers figured out that, the circular CFST members had a more significant concrete confinement effect than the rectangular columns.
+Hu et al.
+2003 [5] and Hu et al.
+2005 [6] had derived the equations to calculate the confined concrete strength under either compression or bending.
+The concrete confinement effect of CFST member was found to be sensitive to its diameter-thickness ratio.
+	\par	
+	Due to the expansion of concrete core, the steel tube of CFST will also be under bi-axial stress state when loaded.
+The multi-axial stress state will change the steel yield stress under compression and tension.
+In the research works of Fujimoto et al.
+2004 [3], Inai et al.
+2004 [4] and Lai and Varma 2016 [7], a reduction of steel yield stress had been made when the CFST was under compression.
+While for the tensile yield stress of steel, Fujimoto et al.
+2004 [3] and Inai et al.
+2004 [4]considered that the bi-axial stress state would have a positive influence on the tensile yield stress of the steel, and thus, an amplification on its value was made.
+	To accurately predict the behaviour of CFST member, the multi-axial stress states should be considered during numerical modelling.
+The 3D Finite Element (FE) model was a numerical model commonly used by many researchers (Hu et al.
+2003 [5], Ellobody et al.
+2006 [8], Duarte et al.
+2016 [9], Lai and Varma 2016 [7] etc.).
+Since the 3D FE model consists with 3D/2D elements, it could take the material strength variation under complex axial stress states into consideration.
+Therefore, the model was proved to be accurate in simulating the response of CFST members under different loading types, namely under axial loading (Hu et al.
+2003 [5], Ellobody et al.
+2006 [8], Duarte et al.
+2016 [9], etc.), under monotonic bending (Hu et al.
+2005 [6], Wang et al.
+2014 [10], etc.) and under cyclic bending (Goto et al.
+2010 [11] and Imani et al.
+2015 [12], etc.).
+
+	Besides the 3D FE model, the Distributed Plasticity (DP) model was also a widely used modelling choice for CFST columns (Han 2004 [13], Tort and Hajjar 2010 [14], Zubydan and ElSabbagh 2011 [15], etc.).
+As the DP model is a simplified numerical solution coupled with fibre element, it could not capture the multi-axial stress states, for both concrete core and steel tube.
+Therefore, the material properties of CFST should be corrected when applying the DP model.
+Almost all the researchers (Han 2004 [13], Fujimoto et al.
+2004 [3], Inai et al.
+2004 [4], Valipour and Foster 2010 [16], Liang et al.
+2006 [17], Tort and Hajjar 2010 [14], Zubydan and ElSabbagh 2011 [15], Lai and Varma 2016 [7], etc.) who worked with DP model had considered the concrete strength under confinement effect.
+But regarding the steel bi-axial stress, only Fujimoto et al.
+2004 [3], Inai et al.
+2004 [4] and Lai and Varma 2016 [7] had considered the its influence on the steel yield stress during modelling.
+The neglecting of steel bi-axial stress states of CFST member may miss leading the analytical results and decrease the accuracy of the DP model.
+	Regarding the Eurocode 4 [18] (EC4) design provision, the confined concrete strength and the corrected steel yield stress are considered.
+However, the code clearly targets this consideration for member under compression, whilst being very restrictive for bending combined with compression.
+When it comes to fully flexural loads, the codes does not consider any effect of multi-axial stress states to exist.
+	As one may have inferred, there is a clear gap in the consideration of multi-axial stress states, including both concrete confinement effect and steel bi-axial stress state, on CFST members under flexural loads.
+The research presented in this paper aims to address this limitation of both the literature and the current design methodologies.
+This paper starts with a brief description of the multi-axial stress states and the verification of previous proposed methods on material strength correction for CFSTs.
+New strength correction methods based on the 3D FE modelling approach, which aims to overcome the limitations of the DP model, was developed and validated.
+By conducting a parametric study on the flexural behaviour of CFST members, closed-form expressions which focus on the calculation the concrete confinement stress and effective steel strength were derived and their feasibility was verified against experimental data.
+
 \end{document}

### 2018-03-26 Paper7.tex
$(data)

@@
 		The paper proposes the methodologies and the equations to consider the influence of multi-axial stress states on material strength of circular Concrete-filled Steel Tubular (CFST) columns.
-From the previous experimental and numerical studies on the flexural behaviour of circular CFST members, the combination of multi-axial stress states, namely the concrete confinement effects and the steel bi-axial stress states, was found to benefit the bending capacity of CFST columns.
+From the previous experimental and numerical studies on the flexural behaviour of circular CFST members, the combination of multi-axial stress states, namely the concrete confinement effects and the steel bi-axial stress state, was found to benefit the bending capacity of CFST columns.
 Therefore, the bending capacity of the CFST columns will be underestimated by the Distributed Plasticity (DP) model when uni-axial material properties are used.
@@
 	The behaviour of concrete-filled steel tubes (CFSTs) is governed by the contribution of the steel tube and the concrete core.
-As concluded from previous experimental studies (\cite{})The concrete core constrains the steel tube to its interior, thus delaying the occurrence of the local buckling to higher levels of deformation and the ductility of the steel tube is improved.
-Besides its excellent ductility, the composition of concrete and steel will also cause the two components under multi-axial stress state and thus, lead to the material properties change.
+As concluded from previous experimental studies (Silva et al.
+2016 \cite{Silva2016}), The concrete core constrains the steel tube to its interior, thus delaying the occurrence of the local buckling to higher levels of deformation and the ductility of the steel tube is improved.
+Besides its excellent ductility, the composition of concrete and steel will also cause the two components under multi-axial stress state and thus, lead to the material properties variance.
 The steel tube provides the confined stress to the concrete core and make it under tri-axial stress state, which is well known as concrete confinement effect.
 The strength and ductility of the concrete core are enhanced by the confinement effect, therefore, the capacity of CFST member under either compression or bending is benefited.
+	\par
 	In recent years, there were many researchers had investigated the concrete confinement effect of CFST members.
 Based on the test results, Sakino et al.
-2004 [2], Fujimoto et al.
-2004 [3] and Inai et al.
-2004 [4] had tested circular and rectangular CFST columns under axial compressive loading, eccentric compressive loading and bending, respectively.
+2004 \cite{RN41}, Fujimoto et al.
+2004 \cite{RN15} and Inai et al.
+2004 \cite{RN30} had tested circular and rectangular CFST columns under axial compressive loading, eccentric compressive loading and bending, respectively.
 All the researchers figured out that, the circular CFST members had a more significant concrete confinement effect than the rectangular columns.
 Hu et al.
-2003 [5] and Hu et al.
-2005 [6] had derived the equations to calculate the confined concrete strength under either compression or bending.
+2003 \cite{RN1} and Hu et al.
+2005 \cite{RN29} had derived the equations to calculate the confined concrete strength under either compression or bending.
 The concrete confinement effect of CFST member was found to be sensitive to its diameter-thickness ratio.
@@
 In the research works of Fujimoto et al.
-2004 [3], Inai et al.
-2004 [4] and Lai and Varma 2016 [7], a reduction of steel yield stress had been made when the CFST was under compression.
+2004 \cite{RN15}, Inai et al.
+2004 \cite{RN30} and Lai and Varma 2016 \cite{RN32}, a reduction of steel yield stress had been made when the CFST was under compression.
 While for the tensile yield stress of steel, Fujimoto et al.
-2004 [3] and Inai et al.
-2004 [4]considered that the bi-axial stress state would have a positive influence on the tensile yield stress of the steel, and thus, an amplification on its value was made.
-	To accurately predict the behaviour of CFST member, the multi-axial stress states should be considered during numerical modelling.
-The 3D Finite Element (FE) model was a numerical model commonly used by many researchers (Hu et al.
-2003 [5], Ellobody et al.
-2006 [8], Duarte et al.
-2016 [9], Lai and Varma 2016 [7] etc.).
-Since the 3D FE model consists with 3D/2D elements, it could take the material strength variation under complex axial stress states into consideration.
-Therefore, the model was proved to be accurate in simulating the response of CFST members under different loading types, namely under axial loading (Hu et al.
-2003 [5], Ellobody et al.
-2006 [8], Duarte et al.
-2016 [9], etc.), under monotonic bending (Hu et al.
-2005 [6], Wang et al.
-2014 [10], etc.) and under cyclic bending (Goto et al.
-2010 [11] and Imani et al.
-2015 [12], etc.).
-
+2004 \cite{RN15} and Inai et al.
+2004 \cite{RN30} considered that the bi-axial stress state would have a positive influence on the tensile yield stress of the steel, and thus, an modification on their values was necessary.
+	\par
 	Besides the 3D FE model, the Distributed Plasticity (DP) model was also a widely used modelling choice for CFST columns (Han 2004 [13], Tort and Hajjar 2010 [14], Zubydan and ElSabbagh 2011 [15], etc.).
@@
 Therefore, the material properties of CFST should be corrected when applying the DP model.
-Almost all the researchers (Han 2004 [13], Fujimoto et al.
-2004 [3], Inai et al.
-2004 [4], Valipour and Foster 2010 [16], Liang et al.
-2006 [17], Tort and Hajjar 2010 [14], Zubydan and ElSabbagh 2011 [15], Lai and Varma 2016 [7], etc.) who worked with DP model had considered the concrete strength under confinement effect.
+All the researchers (Han 2004 [13], Fujimoto et al.
+2004 \cite{RN15}, Inai et al.
+2004 \cite{RN30}, Valipour and Foster 2010 [16], Liang et al.
+2006 [17], Tort and Hajjar 2010 [14], Zubydan and ElSabbagh 2011 [15], Lai and Varma 2016 \cite{RN32}, etc.) who worked with DP model had considered the concrete strength under confinement effect.
 But regarding the steel bi-axial stress, only Fujimoto et al.
-2004 [3], Inai et al.
-2004 [4] and Lai and Varma 2016 [7] had considered the its influence on the steel yield stress during modelling.
+2004 \cite{RN15}, Inai et al.
+2004 \cite{RN30} and Lai and Varma 2016 \cite{RN32} had considered the its influence on the steel yield stress during modelling.
 The neglecting of steel bi-axial stress states of CFST member may miss leading the analytical results and decrease the accuracy of the DP model.
-	Regarding the Eurocode 4 [18] (EC4) design provision, the confined concrete strength and the corrected steel yield stress are considered.
+	\par
+	Regarding the Eurocode 4 \cite{RN64} design provision, the confined concrete strength and the corrected steel yield stress are considered.
 However, the code clearly targets this consideration for member under compression, whilst being very restrictive for bending combined with compression.
 When it comes to fully flexural loads, the codes does not consider any effect of multi-axial stress states to exist.
+	\par
 	As one may have inferred, there is a clear gap in the consideration of multi-axial stress states, including both concrete confinement effect and steel bi-axial stress state, on CFST members under flexural loads.
@@
 
+	\bibliography{../../BibTex/Mine,../../BibTex/CFST,../../BibTex/Eurocode}
+
+	\bibliographystyle{unsrt}
+
 \end{document}

### 2018-03-26 Paper7.tex
mac

@@
 	\begin{abstract}
-		The paper proposes the methodologies and the equations to consider the influence of multi-axial stress states on material strength of circular Concrete-filled Steel Tubular (CFST) columns.
+		The paper proposes the methodologies and the equations to consider the influence of multi-axial stress states on the material strength of circular Concrete-filled Steel Tubular (CFST) columns.
 From the previous experimental and numerical studies on the flexural behaviour of circular CFST members, the combination of multi-axial stress states, namely the concrete confinement effects and the steel bi-axial stress state, was found to benefit the bending capacity of CFST columns.
@@
 As concluded from previous experimental studies (Silva et al.
-2016 \cite{Silva2016}), The concrete core constrains the steel tube to its interior, thus delaying the occurrence of the local buckling to higher levels of deformation and the ductility of the steel tube is improved.
+2016 \cite{Silva2016} and Silva et al.
+2017 \cite{RN140}), The concrete core constrains the steel tube to its interior, thus delaying the occurrence of the local buckling to higher levels of deformation and the ductility of the steel tube is improved.
 Besides its excellent ductility, the composition of concrete and steel will also cause the two components under multi-axial stress state and thus, lead to the material properties variance.
@@
 The strength and ductility of the concrete core are enhanced by the confinement effect, therefore, the capacity of CFST member under either compression or bending is benefited.
-	\par
 In recent years, there were many researchers had investigated the concrete confinement effect of CFST members.
@@
 The concrete confinement effect of CFST member was found to be sensitive to its diameter-thickness ratio.
+Regarding Eurocode 4 \cite{RN64}, the concrete confinement effect of circular CFST members is considered in both compressive and bending cases.
 	\par
-	Due to the expansion of concrete core, the steel tube of CFST will also be under bi-axial stress state when loaded.
-The multi-axial stress state will change the steel yield stress under compression and tension.
-In the research works of Fujimoto et al.
-2004 \cite{RN15}, Inai et al.
-2004 \cite{RN30} and Lai and Varma 2016 \cite{RN32}, a reduction of steel yield stress had been made when the CFST was under compression.
-While for the tensile yield stress of steel, Fujimoto et al.
+	Due to the expansion of the concrete core, the steel tube of CFST will be under bi-axial stress state when the member is loaded.
+The bi-axial stress state will have an influence on the steel yield stress.
+According to the research works of Fujimoto et al.
 2004 \cite{RN15} and Inai et al.
-2004 \cite{RN30} considered that the bi-axial stress state would have a positive influence on the tensile yield stress of the steel, and thus, an modification on their values was necessary.
+2004 \cite{RN30}, the bi-axial stress state was found to have a positive effect on the steel tensile yield stress and a negative influence on the steel  compressive yield stress.
+Regarding the Eurocode 4 \cite{RN64} design provision, it considers a reduction of the steel yield stress when calculating the circular CFST column's plastic resistance to compression.
+While for the consideration of the flexural resistance of the circular CFST member, the Eurocode 4 is very restrictive since the codes does not consider any effect of steel bo-axial stress state to exist.
 	\par
@@
 	\par
-	Regarding the Eurocode 4 \cite{RN64} design provision, the confined concrete strength and the corrected steel yield stress are considered.
-However, the code clearly targets this consideration for member under compression, whilst being very restrictive for bending combined with compression.
-When it comes to fully flexural loads, the codes does not consider any effect of multi-axial stress states to exist.
-	\par
 	As one may have inferred, there is a clear gap in the consideration of multi-axial stress states, including both concrete confinement effect and steel bi-axial stress state, on CFST members under flexural loads.

### 2018-03-27 Paper7.tex
$(data)

@@
-\documentclass[12pt, A4]{article}
+\documentclass[12pt,a4]{article}
 \usepackage{geometry}
+\usepackage{graphicx}
+
 \geometry{margin=1in}
@@
 2004 \cite{RN15} and Inai et al.
-2004 \cite{RN30}, the bi-axial stress state was found to have a positive effect on the steel tensile yield stress and a negative influence on the steel  compressive yield stress.
+2004 \cite{RN30}, the bi-axial stress state would increase the steel yield stress when the CFST member is under tension while descrese the steel yield stress when the member is compressed.
 Regarding the Eurocode 4 \cite{RN64} design provision, it considers a reduction of the steel yield stress when calculating the circular CFST column's plastic resistance to compression.
-While for the consideration of the flexural resistance of the circular CFST member, the Eurocode 4 is very restrictive since the codes does not consider any effect of steel bo-axial stress state to exist.
+While for the consideration of the flexural resistance of the circular CFST member, the Eurocode 4 is very restrictive since the code does not consider any effects of steel bi-axial stress state to exist.
 	\par
-	Besides the 3D FE model, the Distributed Plasticity (DP) model was also a widely used modelling choice for CFST columns (Han 2004 [13], Tort and Hajjar 2010 [14], Zubydan and ElSabbagh 2011 [15], etc.).
+	The Distributed Plasticity (DP) model is a widely used modelling choice for CFST columns.
 As the DP model is a simplified numerical solution coupled with fibre element, it could not capture the multi-axial stress states, for both concrete core and steel tube.
 Therefore, the material properties of CFST should be corrected when applying the DP model.
-All the researchers (Han 2004 [13], Fujimoto et al.
+In recent studies of CFST columns, all the researchers (Han 2004 \cite{RN21}, Fujimoto et al.
 2004 \cite{RN15}, Inai et al.
-2004 \cite{RN30}, Valipour and Foster 2010 [16], Liang et al.
-2006 [17], Tort and Hajjar 2010 [14], Zubydan and ElSabbagh 2011 [15], Lai and Varma 2016 \cite{RN32}, etc.) who worked with DP model had considered the concrete strength under confinement effect.
+2004 \cite{RN30}, Liang et al.
+2006 \cite{RN34}, Valipour and Foster 2010 \cite{RN50}, Tort and Hajjar 2010 \cite{RN46}, Zubydan and ElSabbagh 2011 \cite{RN60}, Lai and Varma 2016 \cite{RN32}, etc.) who worked with DP model had considered the concrete strength under confinement effect.
 But regarding the steel bi-axial stress, only Fujimoto et al.
@@
 	\par
-	As one may have inferred, there is a clear gap in the consideration of multi-axial stress states, including both concrete confinement effect and steel bi-axial stress state, on CFST members under flexural loads.
+	As one may have inferred, there is a clear gap in the consideration of multi-axial stress states, including both concrete confinement effect and steel bi-axial stress state, when model or design the CFST members under flexural loads.
 The research presented in this paper aims to address this limitation of both the literature and the current design methodologies.
-This paper starts with a brief description of the multi-axial stress states and the verification of previous proposed methods on material strength correction for CFSTs.
-New strength correction methods based on the 3D FE modelling approach, which aims to overcome the limitations of the DP model, was developed and validated.
-By conducting a parametric study on the flexural behaviour of CFST members, closed-form expressions which focus on the calculation the concrete confinement stress and effective steel strength were derived and their feasibility was verified against experimental data.
+This paper starts with a brief description of the multi-axial stress states and the verification of the previous proposed material strength correction method for CFSTs.
+Based on the 3D Finite Element (FE) model proposed in Jiang et al.
+2018 [?], New material strength correction methods, which aims to overcome the aforementioned limitations of the DP model, are developed and validated.
+By conducting a parametric study on the flexural behaviour of circular CFST members, closed-form expressions which focus on the calculation of the confined concrete stress and the steel bi-axial steel bi-axial yield stress are derived and their feasibility is verified against experimental data.
 
-	\bibliography{../../BibTex/Mine,../../BibTex/CFST,../../BibTex/Eurocode}
+	\section{Multi-axial Stress States of Circular CFST Members}
+	\subsection{Multi-axial Stress States}
+	When the CFST members are under loading, the composite effects are introduced due to the interaction between concrete core and steel tube.
+Thus, both the concrete and steel are under the multi-axial stress states.
+The confined stress provided by the steel tube makes the concrete core under tri-axial stress state, and thus, caused the concrete confinement effect, which can improve its the strength and ductility.
+Thus, the concrete confinement effect will benefit the flexural capacity of CFST members.
+There were many researchers studied the concrete confinement effect for CFST members in recent years (Han et al.
+2001 \cite{RN23}, Hu et al.
+2003 \cite{RN1}, Hu et al.
+2005 \cite{RN29}, Tort and Hajjar 2010 \cite{RN46} and Lai and Varma 2016 \cite{RN32}) .
+	\par
+	Not only the concrete core, but also the steel tube is under multi-axial stress state.
+The concrete core expands under axial load and the hoop stress (or circumferential stress) is generated around the steel tube.
+As the thickness of the steel tube is relatively small compared to the cross-section diameter, the steel tube could be considered as a shell component.
+Therefore, the material is under bi-axial stress state (Kwan et al.
+2016 \cite{RN31}).
+Figure \ref{fig:1} shows the stress state of the steel tube of circular CFST member.
+Since the CFST member is under bending, part of the steel tube is under compression and part of it is under tension and the influences of bi-axial stress state on the two parts are different.
+As can be seen in Figure \ref{fig:1}, for the compression area, the steel is combined with the compressive stress on vertical direction ($\sigma_2$) and tensile stress on the horizontal direction ($\sigma_1$).
+While for the tension area, the steel is under tensile stress on both vertical and horizontal directions.
+	\par
+	\begin{figure}[h]
+		\centering
+		\includegraphics{Figures/Figure_1.pdf}
+		\caption{Steel bi-axial stress state under bending force}
+		\label{fig:1}
+	\end{figure}
+	\par
+	To consider the steel yield stress variance under bi-axial stress state, the yield surface is introduced (Figure \ref{fig:2}).
+The positive/negative values on the two axes stand for the tensile/compressive stress, respectively.
+The hoop stress ($\sigma_h$) is plotted on the \textit{x} axis and the corresponding steel yield stresses under compression ($f_{yc}$) and tension ($f_{yt}$) are annotated on the yield surface.
+It could be found that, the steel compressive yield stress ($f_{yc}$) is smaller than the uni-axial yield stress ($f_y$), which will have negative influence on the member flexural capacity.
+On the contrary, the steel tensile yield stress ($f_{yt}$) is larger than the uni-axial yield stress ($f_y$), which will benefit the member strength under bending.
+For circular CFST member under centrally compression, the whole steel section is under compression.
+With the influence of bi-axial stress state, the steel yield stress reduces from $f_y$ to $f_{yc}$.
+For this reason, there is a reduction factor introduced in Eurocode 4 \cite{RN64} to reduce the steel yield stress when considering the plastic resistance of circular CFST to compression.
+Regarding the flexural capacity of CFST members, the influence of the steel bi-axial stress state on it depends on the relative areas between the compressive/tensile regions as well as the values of $f_{yt}$ and $f_{yc}$.
+	\par
+	\begin{figure}[h]
+		\centering
+		\includegraphics{Figures/Figure_2.pdf}
+		\caption{Steel yield surface}
+		\label{fig:2}
+	\end{figure}
+	\par
+	The previous research (Jiang et al.
+2018 [?]) had carried out a numerical study on the influence of the multi-axial stress states on the bending capacity of circular CFST columns.
+In the research work, a comprehensive 3D Finite Element (FE) model, which can capture the multi-axial stress states, and a Distributed Plasticity (DP) model, which cannot consider the multi-axial stress states influence, were developed and validated by experimental results from Silva et al.
+2016 \cite{Silva2016}.
+The 3D FE model was proved to be accurate on the flexural behaviour simulation of the circular CFST member, as the solid and shell elements used by the model can consider the concrete and steel strength variation under multi-axial stress states.
+But regarding the DP model, its predicted capacity was found to be always smaller than the test results.
+Considering that the effects caused by multi-axial stress states could not be simulated by the fibre element, the researchers concluded that the combination of multi-axial stress states could benefit the bending behaviour of circular CFST member under bending combined with low/moderate constant axial load.
+	\par
+	To further verify the influence of the steel bi-axial stress state on material strength, the stress versus strain curves of the steel elements located on the same height level are extracted and plotted in Figure \ref{fig:3}.
+The steel uni-axial stress/strain curve is also plotted in the same figure as the reference curve.
+The tensile strain/stress are defined as positive values.
+It could be seen that, the steel compressive yield stress values are less than the uni-axial yield stress and the tensile yield strain is larger than the uni-axial yield stress, which enhances the conclusion obtained from the yield surface.
+	\par
+	\begin{figure}[h]
+		\centering
+		\includegraphics{Figures/Figure_4.pdf}
+		\caption{The vertical stress/strain curves output from the 3D FE model}
+		\label{fig:3}
+	\end{figure}
+	\par
+	\subsection{Previous Studies on Multi-axial Stress State Influence}
+	In the past, there were many researchers had carried out the studies on the prediction of confined concrete strength for CFST members (Han et al.
+2001 \cite{RN23}, Hu et al.
+2003 \cite{RN1}, Hu et al.
+2005 \cite{RN29} and Tort and Hajjar 2010 \cite{RN46} e.t.c).
+But in these researches, the influence of steel bi-axial stress state was ignored.
+Therefore, these derived confined concrete strength equations may result in the inaccuracy of the numerical prediction.
+Lai and Varma 2016 \cite{RN32} had performed a parametric study on CFST members under compressive loading with the consideration of multi-axial stress states.
+The equation to calculate the confined concrete strength had been derived.
+Moreover, the steel compressive yield strength in the research was reduced to $0.9f_y$.
+But regarding the steel tensile yield stress, there was no correction.
+Thus, the proposed material strength correction equations of Lai and Varma 2016 \cite{RN32} were suitable for CFST members subjected to axial compression but not sufficient for members under bending.
+	\par
+	Inai et al.
+2004 \cite{RN30} and Fujimoto et al.
+2004 \cite{RN15} had used the DP model to simulate the bending behaviour of CFST members.
+To consider the influences of multi-axial stress states, they combined the previous researches on the confined concrete strength and the steel bi-axial yield stress (Kato and Nishiyama 1980 \cite{RN139}, Sakino 1994 \cite{RN138}, Nakahara et al.
+1999 \cite{RN137} and Sakino et al.
+1998 \cite{RN135}) and summarized the material strength correction equations for both concrete and steel.
+For circular CFST members, the confined concrete strength is given in Equation (\ref{eq:1}).
+	\par
+	\begin{equation}
+	f_{cc} = f_c + 4.1 \frac{0.38tf_y}{D-2t}
+	\label{eq:1}
+	\end{equation}
+	\par
+	Regarding the steel bi-axial stress state, a constant hoop stress, which equals to $0.19f_y$, was assumed and the steel yield stresses under compression and tension were adopted as $0.91f_y$ and $1.08f_y$, respectively.
+The proposed DP models from Jiang et al.
+2018[?] were re-analysed with the material strengths corrected by these equations to verify their accuracy.
+Table 1 shows the confined concrete strength (fcc) and the corrected steel yield stresses (fyc and fyt).
+
+	\bibliography{../../BibTex/Mine,../../BibTex/CFST,../../BibTex/Eurocode,../../BibTex/Hollow_Sections,../../BibTex/Concrete}
 

### 2018-03-27 Paper7.tex
$(data)

@@
 \usepackage{graphicx}
+\usepackage{amsmath}
 
@@
 2016 \cite{RN31}).
-Figure \ref{fig:1} shows the stress state of the steel tube of circular CFST member.
+Figure \ref{fig-1} shows the stress state of the steel tube of circular CFST member.
 Since the CFST member is under bending, part of the steel tube is under compression and part of it is under tension and the influences of bi-axial stress state on the two parts are different.
-As can be seen in Figure \ref{fig:1}, for the compression area, the steel is combined with the compressive stress on vertical direction ($\sigma_2$) and tensile stress on the horizontal direction ($\sigma_1$).
+As can be seen in Figure \ref{fig-1}, for the compression area, the steel is combined with the compressive stress on vertical direction ($\sigma_2$) and tensile stress on the horizontal direction ($\sigma_1$).
 While for the tension area, the steel is under tensile stress on both vertical and horizontal directions.
@@
 		\caption{Steel bi-axial stress state under bending force}
-		\label{fig:1}
+		\label{fig-1}
 	\end{figure}
 	\par
-	To consider the steel yield stress variance under bi-axial stress state, the yield surface is introduced (Figure \ref{fig:2}).
+	To consider the steel yield stress variance under bi-axial stress state, the yield surface is introduced (Figure \ref{fig-2}).
 The positive/negative values on the two axes stand for the tensile/compressive stress, respectively.
@@
 		\caption{Steel yield surface}
-		\label{fig:2}
+		\label{fig-2}
 	\end{figure}
@@
 	\par
-	To further verify the influence of the steel bi-axial stress state on material strength, the stress versus strain curves of the steel elements located on the same height level are extracted and plotted in Figure \ref{fig:3}.
+	To further verify the influence of the steel bi-axial stress state on material strength, the stress versus strain curves of the steel elements located on the same height level are extracted and plotted in Figure \ref{fig-3}.
 The steel uni-axial stress/strain curve is also plotted in the same figure as the reference curve.
@@
 		\caption{The vertical stress/strain curves output from the 3D FE model}
-		\label{fig:3}
+		\label{fig-3}
 	\end{figure}
@@
 1998 \cite{RN135}) and summarized the material strength correction equations for both concrete and steel.
-For circular CFST members, the confined concrete strength is given in Equation (\ref{eq:1}).
+For circular CFST members, the confined concrete strength is given in Equation (\ref{eq-1}).
 	\par
@@
 	f_{cc} = f_c + 4.1 \frac{0.38tf_y}{D-2t}
-	\label{eq:1}
+	\label{eq-1}
 	\end{equation}
@@
 2018[?] were re-analysed with the material strengths corrected by these equations to verify their accuracy.
-Table 1 shows the confined concrete strength (fcc) and the corrected steel yield stresses (fyc and fyt).
+Table 1 shows the confined concrete strength ($f_{cc}$) and the corrected steel yield stresses ($f_{yc}$ and $f_{yt}$).
+	\par
+	\begin{table}[h]
+		\centering
+		\caption{Corrected material strength for the circular CFST specimens with methololedges from Inai et al. 2004 \cite{RN30} and Fujimoto et al. 2004 \cite{RN15}}
 
-	\bibliography{../../BibTex/Mine,../../BibTex/CFST,../../BibTex/Eurocode,../../BibTex/Hollow_Sections,../../BibTex/Concrete}
+		\label{tb-1}
+	\end{table}
+	\par
+	Figure \ref{fig-4} displays the lateral load versus drift ratio plots comparison of three results, namely the tests results, the DP model results with uni-axial material strength and the DP model results with corrected material strength.
+The four plots on the left column of the figure belong show the response of the CFST specimens with no axial load.
+It could be found that, with the correction methods given by Inai et al.
+2004 \cite{RN30} and Fujimoto et al.
+2004 \cite{RN15}, the accuracy of the DP model had been improved, as good agreements are observed between the DP model with corrected material strength and the test results.
+But regarding the specimens with constant axial loads (plots on the right column), nearly no improvement of the DP model results is found by applying the correction methods, by comparing its results with the original DP model predictions.
+As constant factors were used to correct the steel stress in the correction methods given by the two research works, it could be summarized that the steel bi-axial stress state has a relationship with the axial load level.
+	\par
+	\begin{figure}[h]
+		\centering
+		\includegraphics[height=0.9\textheight]{Figures/Figure_5.pdf}
+		\caption{Lateral load versus drift ratio plots comparison between the test results, the two DP models}
+		\label{fig-4}
+	\end{figure}
+	\par
+	\section{Material Strength Correction Methods}
+	As concluded in the Section 2, the material strength correction methods proposed by previous researchers are not efficient enough to improve the prediction results of the DP model, especially in the cases that the circular CFST members are loaded with lateral force combined with constant axial load.
+Thus, new material strength correction methods should be proposed to account for the influence of the multi-axial stress states on the material strength variance of the circular CFST member.
+Given that the developed 3D FE model (Jiang et al.
+2018 [?]) can accurately represent the flexural behaviour of CFST members, this model is used to calibrate this strength correction methodology.
+In the following paragraphs, the material strength correction methods, which aims to acquire the confined concrete strength ($f_{cc}$) and the steel bi-axial yield stress ($f_{yb}$) from the numerical results given by the 3D FE model, are detailed.
+	\par
+
+	\subsection{Overall Description of the Approach}
+	The material strength correction methods are applied to the base section of the CFST column.
+As the multi-axial stress states have different influences on the concrete and steel properties, the two sections should be analysed in a separate manner.
+For each of the two sections, two steps are followed to get the corrected material strength, namely to address the yield moment of the section and to adopt the equivalent (or average) stress of the section at the yield point.
+Figure \ref{fig-5} shows the schematic diagram of the strength correction methods.
+Taking the advantages of the 3D FE model, the moment-drift and axial force-drift curves of both the concrete section and steel tube section can be extracted from the numerical results, where the drift ratio ($\theta$) is defined as the ratio between the lateral displacement and the CFST column length ($L$).
+It should be noted that, although the individual axial loads applied to the concrete and steel sections change with the increase of the drift ratio, the sum of the axial loads on the two sections is equal to a constant axial load applied to the CFST member.
+Due to the algorithm behind the 3D FE analysis, the outputs of the results are sets of discrete incremental values.
+Thus, the method proposed by Akima 1970 \cite{Akima1970} is introduced to smooth these force-drift curves by interpolation.
+For the two cross-sections, their yield drift ratios ($θ_y^c$ and $θ_y^s$) of the moment-drift plots could be adopted.
+The corresponding section moments ($M_y^c$ and $M_y^s$) and axial loads ($N_y^c$ and $N_y^s$) could be acquired.
+By making reasonable assumptions about the stress distributions on the concrete and steel sections, which are described in Sections 3.3, the equivalent stresses of the two sections at the yield points could be calculated based on the section force equilibrium.
+The two adopted equivalent stresses are taken as the corrected material strengths.
+In the following sections, the correction methods for each of the member parts are detailed.
+	\par
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=\textwidth]{Figures/Figure_6.pdf}
+		\caption{Material strength correction methods schematic diagram}
+		\label{fig-5}
+	\end{figure}
+	\par
+
+	\subsection{Yield Points of the Concrete and Steel Sections}
+	The yield moments of the concrete core and the steel tube are directly related to their material strengths, namely the confined concrete strength and the steel bi-axial yield stress.
+Thus, to acquire the corrected material strengths, the yield points of the two sections should be addressed first.
+Figure \ref{fig-6} shows the moment-drift ratio curves of the concrete section.
+The shape of the moment-drift ratio curve can be classified into two types.
+For the concrete core with a relatively high confined stress, not only its strength, but also its ductility is remarkably increased.
+Thus, the corresponding moment-drift ratio curve shows no strength degradation at plastic range, as can be seen in Figure \ref{fig-6} (a).
+While for the concrete core under low/moderate confinement effect, although its strength and ductility are improved by the confined stress, the confined stress level is not enough to eliminate the influence of the concrete cracks.
+Thus, there is still strength degradation exhibited in the corresponding moment-drift ratio curve (Figure \ref{fig-6} (b)).
+For the two conditions, the correction methods are slightly different.
+	\par
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=\textwidth]{Figures/Figure_7.pdf}
+		\caption{The moment versus drift ratio curves of the concrete core (a) under relatively high confined stress; (b) under relatively low/moderate confined stress}
+		\label{fig-6}
+	\end{figure}
+	\par
+	The method to find the yield point of the concrete section is proposed by ECCS 1986 \cite{RN88}, which used the tangent value to adopt the yield force and displacement of the curve.
+As marked in Figure \ref{fig-6} (a) and (b), the point ($θ_y^c$, $M_y^c$), which has the tangent value equalling to 10\% of the initial slope of the curve, is adopted as the yield point of the concrete section.
+Regarding the initial slope, its value equals to the slope of the line which connects the point with $0.4M_{max}^c$ strength to the coordinate origin.
+For the concrete core with the moment-drift ratio curve type shown in Figure \ref{fig-6} (a), the axial load $N_y^c$ corresponding to drift ratio $θ_y^c$ could be adopted and the axial load and moment pair ($N_y^c$, $M_y^c$) is taken as the section force to acquire the confined concrete strength $f_{cc}$, which is detailed in Section 3.3.
+Regarding the concrete core with the moment-drift ratio curve type similar to the Figure \ref{fig-6} (b), the influence of the section strength degradation should be considered.
+The yield moment $M_y^c$ should be compared with the residual moment $M_{res}^c$.
+If the residual moment $M_{res}^c$ is smaller than the yield moment $M_y^c$, the axial load and moment pair ($N_{res}^c$, $M_{res}^c$) should be taken as the section forces to adopt the confined concrete strength instead of using force pair ($N_y^c$, $M_y^c$).
+By taking into account the influence of the residual moment $M_{res}^c$, the acquired confined concrete strength should stay at the safe side.
+	\par
+	Figure \ref{fig-7} shows the moment-drift ratio curve of the steel cross-section.
+As can be seen, the method of adopting the yield point of the steel cross-section is similar to the method applied for the concrete core, which makes use of the tangent value.
+The moment-drift ratio curve of the steel cross-section shows good ductility due to the constraint effects of the concrete core.
+The influence of residual strength can be neglected and the force pair ($N_y^s$, $M_y^s$) is used to adopt the steel bi-axial stress, which is described in the following section.
+	\par
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.5\textwidth]{Figures/Figure_8.pdf}
+		\caption{The moment versus drift ratio curves of the steel tube cross-section}
+		\label{fig-7}
+	\end{figure}
+	\par
+	\subsection{Corrected Material Strength}
+	With the yield points adopted from Section 3.3, the corrected material strengths of the concrete and the steel can be obtained by conducting section analysis.
+As observed in Jiang et al.
+2018 [?], for CFSTs under flexural loading, the stress distributions on the cross-sections are non-uniform.
+Due to this non-uniformity, it may be difficult to pinpoint the location of the neutral axis of the cross-section.
+Thus, although the stress distribution on the two sections could be extracted from the numerical results easily, it is not recommended to adopt the corrected material strengths from the non-uniform distributed stress.
+Therefore, to perform any material strength correction, the non-uniform stress distribution should be “converted” into a uniform distribution of stresses for both sections.
+Figure \ref{fig-8} shows the simplified stress blocks of the concrete and steel tube sections according to the assumptions made in Section 3.3.1 and 3.3.2.
+The uniform distributed stress values of on the concrete and the steel cross-sections, which represent the average stress on the two sections, are adopted as the corrected material strengths of the CFST member.
+In the following subchapters, an indirect approach is proposed to obtain the corrected material strengths of the concrete and steel sections.
+	\par
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.75\textwidth]{Figures/Figure_9.pdf}
+		\caption{The simplified stress distribution of the concrete and steel sections}
+		\label{fig-8}
+	\end{figure}
+	\par
+	\subsubsection{Corrected Material Strength of Concrete}
+	Regarding the concrete core, the following assumptions are made:
+	\begin{itemize}
+		\item The cross-section has reached a full plasticity state;
+
+		\item The tensile strength of the concrete is neglected, since it is relatively low compared to the compressive strength, and in the likely event of cracking, no stresses will develop in the tensile region;
+
+		\item The confined concrete stresses are uniformly distributed in the compressive region with a value of $f_{cc}$, which is the equivalent stress shown in Figure \ref{fig-8};
+
+		\item The neutral axis is a straight line parallel to the bending axis, i.e.
+perpendicular to the lateral loading direction.
+The distance from the neutral axis to the major axis of the section is $h_c$, which ranges from $−0.5D_c$ to $0.5D_c$, as shown in Figure \ref{fig-8}.
+	\end{itemize}
+	Based on equilibrium of axial loads and moments shown in Equation (\ref{eq-2}) and supplementary Equations (\ref{eq-3}) to (\ref{eq-5}), the confined concrete strength, $f_{cc}$, could be calculated.
+	\begin{equation}\label{eq-2}
+	\left\{
+	\begin{aligned}
+	&N_y^c + A_{cc}f_{cc}  & = 0\\
+	&M_y^c + A_{cc}f_{cc}h_{cc} & = 0
+	\end{aligned}
+	\right.
+	\textrm{ or }
+	\left\{
+	\begin{aligned}
+	&N_{res}^c + A_{cc}f_{cc} & = 0\\
+	&M_{res}^c + A_{cc}f_{cc}h_{cc} & = 0
+	\end{aligned}
+	\right.
+	\end{equation}
+
+	\begin{equation}\label{eq-3}
+	A_{cc} = \frac{1}{4}\theta_{c}D_{c}^2 + \dfrac{1}{2}h_cD_c\sin\theta_c
+	\end{equation}
+
+	\begin{equation}\label{eq-4}
+	h_{cc} = \frac{2(\frac{D_c^2}{4} - h_c^2)^\frac{3}{2}}{3A_{cc}}
+	\end{equation}
+
+	\begin{equation}\label{eq-5}
+	\theta_c = \cos^{-1}{\frac{2h_c}{D_c}}
+	\end{equation}
+	\par
+	\subsubsection{Corrected Material Strength of Steel}
+	As concluded in Section 2.1, the steel bi-axial stress state will make the steel has different yield stresses under compression and tensile force.
+But in modelling or design of CFST members, it is no common to consider the steel compressive and tensile yield stresses individually.
+Thus, the average stress of the steel section at yield point, which is  the uniform distributed stress value in \ref{fig-8}, is adopted to represent the steel bi-axial stress ($f_{yb}$).
+To perform the strength correction method, the following assumptions about the stress distribution on the steel section are made:
+	\begin{itemize}
+		\item The whole cross-section is in plasticity state;
+
+		\item Compressive and tensile stresses are assumed to have the same absolute value, $f_{yb}$, which is the steel bi-axial yield stress;
+
+		\item The neutral axis is a straight-line parallel to the bending axis.
+The distance from the neutral axis to the major axis of the section is hs, which ranges from $−0.5D$ to $0.5D$, as shown in Figure \ref{fig-8}.
+	\end{itemize}
+	\par
+	Based on equilibrium of axial loads and moments shown in Equation (6) and the corresponding supplementary Equations (7) to (16), the steel bi-axial yield stress, $f_{yb}$, could be calculated as:
+
+	\subsection{Validation of the Correction Methods}
+	In order to validate the proposed material strength correction methods for circular CFST members, the eight specimens used in Section 2.2 were applied with the methods.
+The original and the corrected material strengths are listed in Table \ref{tb-2}.
+It could be found that, both the concrete and the steel yield strengths are increased by the proposed correction methods, which is in line with the conclusion that the multi-axial stress states will have a positive influences on the flexural capacity of the circular CFST member.
+	\par
+	\begin{table}
+		\caption{Corrected material strengths from the correction methods}
+		\label{tb-2}
+	\end{table}
+	\par
+	The eight specimens are re-analysed by the DP model with the material strengths given by the correction methods.
+As discussed in Section 3.2, the correction methods has already taken the influence of concrete residual strength into consideration during correction procedure.
+Thus, the acquired confined concrete strength stays at the safe side and there is no need to consider the softening of the concrete strength for a second time.
+Therefore, the confined concrete constitution law used in DP model is defined as a perfect elasto-plastic curve.
+The obtained lateral force-drift curves of the eight specimens are shown in Figure \ref{fig-9}.
+For each member, the numerical results of the DP model with both the uncorrected and corrected material properties (labelled with $FE_{DP}$ and 〖$FE_{DP}^{Method}$, respectively) are plotted against the results of the 3D FE model (labelled with $FE_{3D}$).
+	\par
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.85\textwidth]{Figures/Figure_10.pdf}
+		\caption{Lateral force-drift ratio curves of the test results and the two DP analyses}
+		\label{fig-9}
+	\end{figure}
+	\par
+	Analysis of the results shown in Figure \ref{fig-9} allow concluding that the computation of material strength corrections in the DP model leads to a very good agreement the results from the 3D FE model.
+This is further supported by comparing the peak lateral loads, as shown in Table \ref{tb-3}.
+In the table, the maximum lateral forces of the DP models ($F_{DP}$ for the uni-axial material strengths and $F_{DP}^{Method}$ for the corrected material strengths), are compared with the value from the 3D FE model, $F_{3D}$.
+The ratios between the ultimate values of the 3D FE model and the DP models, $F_{DP}/F_{3D}$ and $F_{DP}^{Method}/F_{3D}$, are also shown.
+As one may infer from the analysis of Table \ref{tb-3}, by correcting the material strength, the average differences between the 3D FE model and the DP model decrease from 12\% to 3\%.
+Thus, it can be concluded that the strength correction method could greatly enhance the accuracy of the DP modelling approach.
+	\par
+	\begin{table}
+		\caption{Effect of strength corrections on DP modelling peak flexural capacities}
+		\label{tb-3}
+	\end{table}
+	\par
+	\section{Material Strength Correction Equations}
+	Although the correction of material strength could improve the accuracy of the DP model, the drawback is obvious: one should conduct a detailed numerical analysis (e.g.
+3D FE model) before any other analysis.
+Although, in principle, this works for any CFST, the process itself lacks efficiency when extrapolated to a large number of members.
+Thus, the development of a material strength correction database, in the form of member property-dependent equations, is particularly relevant, since detailed modelling procedures need not be carried-out again.
+In the following sections, a comprehensive parametric study, aims at the development of such material strength correction database, is described.
+The statistic procedure is taken and the material strength correction equations, which is independent on the 3D FE model, are derived.
+	\subsection{Parametric Study}
+	To carry out the parametric study, a number of parameters that define both the properties of the CFST member and the load conditions were considered: 1) diameter-to-thickness ratio of the steel tube; 2) concrete uni-axial compressive strength; 3) steel uni-axial yield stress and 4) axial load level.
+As shown in Table \ref{tb-4}, eleven steel tubes were adopted, between high and moderate values of diameter-to-thickness ratio.
+The length of the tube is fixed to six times its diameter.
+Four different steel grades, namely S235, S355, S420 and S690, are adopted and combined with the eleven steel tubes types.
+For each steel grade, two different concrete strengths were considered, namely $0.1f_y$ and $0.2f_y$, and the value is limited to a maximum of $100MPa$.
+As a combination of the previous material parameters with the considered steel tubes, a total of 88 CFST members were adopted for the parametric study.
+	\par
+	\begin{table}
+		\caption{Steel tubes of the parametric study}
+		\label{tb-4}
+	\end{table}
+	\par
+	The axial load level will play an important role to the corrected material strength, as the increase of the axial load will result in the change of location of the neutral axis.
+Thus, five different axial load levels, $μ_n$, are adopted, namely 0\% (no axial load), 5\%, 10\%, 20\% and 30\%.
+The axial load level is defined as the portion of the plastic axial strength of the cross-section, calculated with Equation (17).
+	\par
+	By combining the 88 CFST columns with the 5 axial load levels, 440 monotonic flexural analysis were conducted.
+Each of the columns was laterally loaded up to a drift ratio level of 7\%.
+For all the columns, the material strength correction methods described in Section 3 were applied.
+Thus, a material strength database consisting of 440 CFST members was created.
+	\par
+	In order to represent the wide set of members with a single representative parameter, a section factor, $ξ$, is adopted, as shown in Equation (18).
+In a simplified manner, the section factor consists the cross-section slenderness, $D/t$, unconfined concrete strength, $f_c$, and uni-axial steel yield stress $f_y$.
+For CFST members with given concrete and steel types, the larger values of $ξ$ indicate a stronger concrete core and a weaker steel tube, and vice versa.
+	\subsection{Strength Correction Equations for Concrete}
+	Regarding the strength corrections of the concrete core, the ratio between the confined and plain strength values, $f_{cc}/f_c$, are plotted against section factor $ξ$ in Figure \ref{fig-10}.
+The scatters of the CFST members are grouped according to the axial load levels ,$μ_n$, and are classified in different colours.
+Analysis of the results allows concluding that regardless of the axial load level, the values of $f_{cc}/f_c$ were consistently larger than 1.0.
+This confirms the development of confinement in the concrete core, which increases the strength of the concrete material.
+Also clear is that as $ξ$ increases, $f_{cc}/f_c$ decreases.
+This is in line with the common notion that the higher the cross-section slenderness (which is proportional $ξ$), the least significant will the confinement effect of the concrete core be.
+	\par
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.85\textwidth]{Figures/Figure_11.pdf}
+		\caption{Distribution of confined concrete strengths for each axial load level}
+		\label{fig-10}
+	\end{figure}
+	\par
+	It could also be found that, the scatter distributions of different axial load levels trended to be similar.
+This indicates that the confinement effect of the concrete core does not depend on the axial load level, for flexural loading scenarios.
+From the Figure \ref{fig-10}, it may also be assumed that the relationship between $f_{cc}/f_c$ and $ξ$ is linear.
+Thus, for the condition that the column is under flexural force, the confined concrete strength function of circular CFST member is proposed as Equation (19).
+It should be noted that, in Figure \ref{fig-10}, there are 84\% of the scatted points  staying above the proposed equation line, which indicates that the confined concrete strength function can reduce the possibility of overestimating the confined concrete strength.
+It should be highlighted that, as concluded by Hu et al.
+2003 \cite{RN1} and Hu et al.
+2005 \cite{RN29}, for CFST members under centrally compression and flexural force, the confined strength of the concrete core should be different.
+Thus, the proposed confined concrete strength equation only applies to the case that the circular CFST column is under bending combined with constant axial load.
+	\subsection{Strength Correction Equations for Steel}
+	Similar to the corrections of the concrete, the ratio between the steel bi-axial yield stress and uni-axial yield stress, $f_{yb}/f_y$, are plotted against $ξ$ in Figure \ref{fig-11} for each $μ_n$.
+Analysis of the results shown in $f_{yb}/f_y$ allows concluding that similarly to the values for concrete, regardless of the axial load level, the values of fyb/fy were always larger than 1.0.
+This indicates the development of bi-axial stress state for circular CFST members under moderate/low axial load level, which benefits the member flexural capacity.
+Also clear is that the axial load has a negative influence on the stress state effect, as the steel bi-axial yield stress decreases with the increase of $μ_n$.
+This enhances the conclusion from Section 2.2 that the axial load level will affect the steel bi-axial stress state.
+	\par
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=\textwidth]{Figures/Figure_12.pdf}
+		\caption{Distribution of steel bi-axial yield strength for each axial load level}
+		\label{fig-11}
+	\end{figure}
+	\par
+	It can be observed that all the five sets of scatters have a linear trend.
+Thus, the least-square linear regressions are applied to the scatters of five axial load levels.
+The corresponding regression line coefficients $a_s$ and $b_s$ of the five sets of data are listed in Table \ref{tb-5}.
+Based on the regression lines, the material strength equation for the steel is proposed.
+As expressed in Equation (20), the equation is generated by shifting the regression line downward by a value of $c_s$.
+The $c_s$ values, which will make about 84\% of the scatters above the strength equation line of each axial load level, are listed in Table \ref{tb-5}.
+The main purpose of introduce the parameter $c_s$ is to reduce the possibility of overestimating the steel bi-axial stress and thus, make the material correction equation stay at the safe side.
+	\par
+	For one CFST column of a given axial load level, the coefficients $a_s$, $b_s$ and $c_s$ values can be adopted by conducting linear interpolation of axial load level $μ_n$ in Table \ref{tb-5}.
+It should be highlighted that the equation only applies for circular CFST member with axial load level less than or equal to 30\%.
+	\par
+	\begin{table}
+		\caption{The coefficients $a_s$, $b_s$ and $c_s$ values for each axial load level}
+		\label{tb-5}
+	\end{table}
+	\par
+	\subsection{Validation of Strength Correction Equations}
+	In order to validate the Equations (19), (20), the DP models in Section 2.2 were remodelled using the strength given by the proposed equations.
+The corrected material strengths are calculated from the expressions and are listed in Table \ref{tb-6}.
+	\par
+	\begin{table}
+		\caption{Corrected material strengths from the correction equations}
+		\label{tb-6}
+	\end{table}
+	\par
+	The obtained lateral force-drift ratio curves of the eight specimens are shown in Figure \ref{fig-12}.
+For each member, the numerical results of the DP model with both the uni-axial and corrected material properties (labelled with $FE_{DP}$ and $FE_{DP}^{Eq}$, respectively) are plotted against the results of the experimental tests.
+Analysis of the results shown in Figure \ref{fig-12} allow concluding that the computation of DP model (with the use of the material strength correction equations) leads to a good agreement against the experimental results.
+In general, there is an increase of the bending capacity of the CFST member when the material strength correction is considered, compared with the DP model with the uni-axial properties.
+In terms of accuracy, the DP model with corrected strength fits better with the experimental data, especially in the post-yield stage.
+	\par
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.8\textwidth]{Figures/Figure_13.pdf}
+		\caption{Comparison of the flexural behaviour between the two DP models and the experimental evidence}
+		\label{fig-12}
+	\end{figure}
+	\par
+	The benefits of applying the material strength correction equations is further supported by comparing the peak test and numerical lateral loads, as shown in Table \ref{tb-7}.
+In the table, the maximum lateral forces of the DP models, $F_{DP}$ for the uncorrected material strengths and $F_{DP}^{Eq}$ for the corrected material strengths with the use of regression equations, are compared with the values from experimental tests, $F_{test}$.
+The ratio between the values of the test and the DP models, $F_{DP}/F_{test}$ and $F_{DP}^{Eq}/F_{test}$, are also shown.As one may infer from Table \ref{tb-7}, by correcting the material strength with the proposed strength correction equations, the average differences between the test results and the DP model decrease from 11\% to 1\%.
+	\par
+	\begin{table}
+		\caption{Comparison of peak flexural capacities between the DP models and the experimental evidence}
+		\label{tb-7}
+	\end{table}
+	\par
+	Also important is to compare how the peak bending moment measured in the tests, $M_{test}$, compares with the value from the Eurocode 4 with and without material strength corrections ($M_{EC4}$ and $M_{EC4}^{Eq}$, respectively).
+The results obtained are shown in Table \ref{tb-8}.
+Analysis of the results shown in Table \ref{tb-8} allow concluding that by computing the corrected material strengths into the design methodology of Eurocode 4, the average differences between the code and the experimental evidence reduce from 24\% to 15\%.
+The design values of all specimens are still lower than the test results, which indicates that this methodology is still on the conservative side.
+By comparing the experimental results, with the DP model and the design approach of Eurocode 4, both with the corrected material strengths, the significance and validity of the proposed material strength correction equations is clear.
+	\par
+	\begin{table}
+		\caption{Comparison of flexural capacities between Eurocode 4 (with and without strength correction) and experimental evidence}
+		\label{tb-8}
+	\end{table}
+	\par
+	\section{Conclusions}
+	This research paper has described the development of multi-axial stress states, namely the concrete confinement effects and steel bi-axial stress state, which were existing in CFST member.
+The influence of the multi-axial stress states on the bending capacity of circular CFST member had been verified via experimental and numerical studies.
+Based on the 3D FE model, material strength correction methods were developed.
+By conducting a parametric study consisting of 440 CFST members under flexural loading, combined with different levels of axial load, section factor-dependent material strength correction equations were derived.
+Within the scope of the results obtained, the following conclusions can be withdrawn:
+	\begin{itemize}
+		\item The development of multi-axial stress states in circular CFST members may significantly enhance the flexural strength of the members.
+This is somehow neglected with the current design guidelines of Eurocode 4, given that the code only accounts for the development of confinement and not the bi-axial stress state of the steel tube walls;
+
+		\item In order to overcome the limitations of the DP model, a material strength correction method, which basically produces the ratio of required increase of the uniaxial material properties, is devised and calibrated against the results of the detailed 3D FE model.
+The approach proved to improve the accuracy of the DP model;
+
+		\item Based on the parameteric study, it is found that the confined concrete strength can be considered to be independent from the axial load level, for cases that the circular CFST members are under flexural forces and the constant axial load level is less than 30\%.
+
+		\item The development of confinement on the concrete core decreases as the proposed section factor, $ξ$, increases.
+
+		\item For the steel tube, it is found that the development of a bi-axial stress state on the steel tube walls may increase the uniaxial strength of the material when the axial load level $μ_n$ is less than 30\%.
+The increase in axial load level is found to have a detrimental effect on the influence the bi-axial stress state;
+
+		\item Given the results of the parametric study, $ξ$ and $μ_n$ dependent material strength correction equations were derived to account for the development of multi-axial stress states on both parts of circular CFST members under flexural force.
+
+		\item Both proposed material correction equations were validated against experimental evidence, and found to provide improve the accuracy of both simplified modelling and design procedures.
+By comparing with the experimental tests shown in the paper, the average differences between the peak flexural capacities of the test specimens and the distributed plasticity model decrease from 11\% to 1\%, without and with the application of the proposed material strength correction equations, respectively.
+Moreover, computing the corrected material strengths in the design methodology of EC4 leads to a reduction in the average differences between the code and the experimental evidence from 24\% to 15\%, without and with the application of the proposed material strength correction equations, respectively.
+	\end{itemize}
+
+	\bibliography{../../BibTex/Mine,../../BibTex/CFST,../../BibTex/Eurocode,../../BibTex/Hollow_Sections,../../BibTex/Concrete,../../BibTex/Basic_Theory,../../BibTex/Loading_Protocol}
 

### 2018-03-28 Paper7.tex
$(data)

@@
 
-\title{Influence of Multi-Axial Stress States on the Flexural Behaviour of Circular Concrete-Filled Steel Tubes}
+\title{Assessment of Multi-Axial Stress State effects of Circular Concrete-Filled Steel Tubular Columns under Flexural Loading}
 \author{Yadong Jiang \and António Silva \and Bledar Kalemia \and José Miguel Castro \and Ricardo Monteiro}
@@
 		The paper proposes the methodologies and the equations to consider the influence of multi-axial stress states on the material strength of circular Concrete-filled Steel Tubular (CFST) columns.
-From the previous experimental and numerical studies on the flexural behaviour of circular CFST members, the combination of multi-axial stress states, namely the concrete confinement effects and the steel bi-axial stress state, was found to benefit the bending capacity of CFST columns.
-Therefore, the bending capacity of the CFST columns will be underestimated by the Distributed Plasticity (DP) model when uni-axial material properties are used.
-To account for the material strength variation under multi-axial stress states and to improve the accuracy of the DP model, material strength correction methods were proposed based on the analytical results given by the 3D Finite Element (FE) model.
-A comprehensive parametric study, which involved a wide range of diameter-thickness ratios, material properties and axial load levels, had been carried out to study the influence of CFST cross-section properties on the multi-axial stress states.
-Based on the parametric study, the confined concrete strength under bending was found to be independent on the constant axial load level.
-On the contrary, the steel bi-axial stress was proved to be sensitive to the constant axial load level.
-A section factor $\xi$ was used to represent both the geometry and material properties of a CFST cross-section.
-With statistic operations, $\xi$-dependent correction equations were derived to account for the material strength variation under multi-axial stress states.
-The feasibility of the proposed material strength correction equations was verified to be good for both the design and modelling of circular CFST members.
+The combination of multi-axial stress states, namely the concrete confinement effects and the steel bi-axial stress state, is found to benefit the bending capacity of circular CFST columns.
+Therefore, to account for the material strength variation under multi-axial stress states and to improve the accuracy of the previous proposed Distributed Plasticity (DP) model, material strength correction methods are proposed based on the analytical results given by the 3D Finite Element (FE) model.
+A comprehensive parametric study, which involved a wide range of diameter-thickness ratios, material properties and axial load levels, has been carried out to study the influence of CFST cross-section properties on the multi-axial stress states.
+Based on the parametric study, the confined concrete strength under bending is found to be independent of the constant axial load level.
+On the contrary, the steel bi-axial stress is proved to be sensitive to the cross-section axial load.
+A section factor $\xi$ is used to represent both the geometry and material properties of a CFST cross-section.
+With statistic operations, $\xi$-dependent correction equations are derived to account for the material strength variation under multi-axial stress states.
+The feasibility of the proposed material strength correction equations is verified to be good for both the design and modelling of circular CFST members.
 	\end{abstract}
@@
 Besides its excellent ductility, the composition of concrete and steel will also cause the two components under multi-axial stress state and thus, lead to the material properties variance.
-The steel tube provides the confined stress to the concrete core and make it under tri-axial stress state, which is well known as concrete confinement effect.
+The steel tube provides the confining stress to the concrete core and makes it under tri-axial stress state, which is well known as concrete confinement effect.
 The strength and ductility of the concrete core are enhanced by the confinement effect, therefore, the capacity of CFST member under either compression or bending is benefited.
@@
 2004 \cite{RN15} and Inai et al.
-2004 \cite{RN30}, the bi-axial stress state would increase the steel yield stress when the CFST member is under tension while descrese the steel yield stress when the member is compressed.
+2004 \cite{RN30}, the bi-axial stress state would increase the steel yield stress when the CFST member is under tension while decrease the steel yield stress when the member is compressed.
 Regarding the Eurocode 4 \cite{RN64} design provision, it considers a reduction of the steel yield stress when calculating the circular CFST column's plastic resistance to compression.
@@
 2004 \cite{RN15}, Inai et al.
-2004 \cite{RN30} and Lai and Varma 2016 \cite{RN32} had considered the its influence on the steel yield stress during modelling.
+2004 \cite{RN30} and Lai and Varma 2016 \cite{RN32} had considered its influence on the steel yield stress during modelling.
 The neglecting of steel bi-axial stress states of CFST member may miss leading the analytical results and decrease the accuracy of the DP model.
@@
 The research presented in this paper aims to address this limitation of both the literature and the current design methodologies.
-This paper starts with a brief description of the multi-axial stress states and the verification of the previous proposed material strength correction method for CFSTs.
+This paper starts with a brief description of the multi-axial stress states and the verification of the previously proposed material strength correction method for CFSTs.
 Based on the 3D Finite Element (FE) model proposed in Jiang et al.
@@
 2003 \cite{RN1}, Hu et al.
-2005 \cite{RN29}, Tort and Hajjar 2010 \cite{RN46} and Lai and Varma 2016 \cite{RN32}) .
+2005 \cite{RN29}, Tort and Hajjar 2010 \cite{RN46} and Lai and Varma 2016 \cite{RN32}).
 	\par
-	Not only the concrete core, but also the steel tube is under multi-axial stress state.
+	Not only the concrete core but also the steel tube is under multi-axial stress state.
 The concrete core expands under axial load and the hoop stress (or circumferential stress) is generated around the steel tube.
@@
 Since the CFST member is under bending, part of the steel tube is under compression and part of it is under tension and the influences of bi-axial stress state on the two parts are different.
-As can be seen in Figure \ref{fig-1}, for the compression area, the steel is combined with the compressive stress on vertical direction ($\sigma_2$) and tensile stress on the horizontal direction ($\sigma_1$).
+As can be seen in Figure \ref{fig-1}, for the compression area, the steel is combined with the compressive stress on the vertical direction ($\sigma_2$) and tensile stress on the horizontal direction ($\sigma_1$).
 While for the tension area, the steel is under tensile stress on both vertical and horizontal directions.
@@
 The hoop stress ($\sigma_h$) is plotted on the \textit{x} axis and the corresponding steel yield stresses under compression ($f_{yc}$) and tension ($f_{yt}$) are annotated on the yield surface.
-It could be found that, the steel compressive yield stress ($f_{yc}$) is smaller than the uni-axial yield stress ($f_y$), which will have negative influence on the member flexural capacity.
-On the contrary, the steel tensile yield stress ($f_{yt}$) is larger than the uni-axial yield stress ($f_y$), which will benefit the member strength under bending.
-For circular CFST member under centrally compression, the whole steel section is under compression.
+It could be found that the steel compressive yield stress ($f_{yc}$) is smaller than the uniaxial yield stress ($f_y$), which will have a negative influence on the member flexural capacity.
+On the contrary, the steel tensile yield stress ($f_{yt}$) is larger than the uniaxial yield stress ($f_y$), which will benefit the member strength under bending.
+For circular CFST member under central compression, the whole steel section is under compression.
 With the influence of bi-axial stress state, the steel yield stress reduces from $f_y$ to $f_{yc}$.
@@
 	To further verify the influence of the steel bi-axial stress state on material strength, the stress versus strain curves of the steel elements located on the same height level are extracted and plotted in Figure \ref{fig-3}.
-The steel uni-axial stress/strain curve is also plotted in the same figure as the reference curve.
+The steel uniaxial stress/strain curve is also plotted in the same figure as the reference curve.
 The tensile strain/stress are defined as positive values.
-It could be seen that, the steel compressive yield stress values are less than the uni-axial yield stress and the tensile yield strain is larger than the uni-axial yield stress, which enhances the conclusion obtained from the yield surface.
+It could be seen that the steel compressive yield stress values are less than the uniaxial yield stress and the tensile yield strain is larger than the uniaxial yield stress, which enhances the conclusion obtained from the yield surface.
 	\par
@@
 2005 \cite{RN29} and Tort and Hajjar 2010 \cite{RN46} e.t.c).
-But in these researches, the influence of steel bi-axial stress state was ignored.
+But in these research works, the influence of steel bi-axial stress state was ignored.
 Therefore, these derived confined concrete strength equations may result in the inaccuracy of the numerical prediction.
@@
 	\par
-	Figure \ref{fig-4} displays the lateral load versus drift ratio plots comparison of three results, namely the tests results, the DP model results with uni-axial material strength and the DP model results with corrected material strength.
+	Figure \ref{fig-4} displays the lateral load versus drift ratio plots comparison of three results, namely the tests results, the DP model results with uniaxial material strength and the DP model results with corrected material strength.
 The four plots on the left column of the figure belong show the response of the CFST specimens with no axial load.
@@
 	\section{Material Strength Correction Methods}
-	As concluded in the Section 2, the material strength correction methods proposed by previous researchers are not efficient enough to improve the prediction results of the DP model, especially in the cases that the circular CFST members are loaded with lateral force combined with constant axial load.
+	As concluded in Section 2, the material strength correction methods proposed by previous researchers are not efficient enough to improve the prediction results of the DP model, especially in the cases that the circular CFST members are loaded with lateral force combined with a constant axial load.
 Thus, new material strength correction methods should be proposed to account for the influence of the multi-axial stress states on the material strength variance of the circular CFST member.
@@
 The shape of the moment-drift ratio curve can be classified into two types.
-For the concrete core with a relatively high confined stress, not only its strength, but also its ductility is remarkably increased.
-Thus, the corresponding moment-drift ratio curve shows no strength degradation at plastic range, as can be seen in Figure \ref{fig-6} (a).
+For the concrete core with a relatively high confining stress, not only its strength but also its ductility is remarkably increased.
+Thus, the corresponding moment-drift ratio curve shows no strength degradation at the plastic range, as can be seen in Figure \ref{fig-6} (a).
 While for the concrete core under low/moderate confinement effect, although its strength and ductility are improved by the confined stress, the confined stress level is not enough to eliminate the influence of the concrete cracks.
@@
 If the residual moment $M_{res}^c$ is smaller than the yield moment $M_y^c$, the axial load and moment pair ($N_{res}^c$, $M_{res}^c$) should be taken as the section forces to adopt the confined concrete strength instead of using force pair ($N_y^c$, $M_y^c$).
-By taking into account the influence of the residual moment $M_{res}^c$, the acquired confined concrete strength should stay at the safe side.
+By taking into account the influence of the residual moment $M_{res}^c$, the acquired confined concrete strength should stay on the safe side.
 	\par
 	Figure \ref{fig-7} shows the moment-drift ratio curve of the steel cross-section.
-As can be seen, the method of adopting the yield point of the steel cross-section is similar to the method applied for the concrete core, which makes use of the tangent value.
+As can be seen, the method of adopting the yield point of the steel cross-section is similar to the method applied to the concrete core, which makes use of the tangent value.
 The moment-drift ratio curve of the steel cross-section shows good ductility due to the constraint effects of the concrete core.
@@
 Figure \ref{fig-8} shows the simplified stress blocks of the concrete and steel tube sections according to the assumptions made in Section 3.3.1 and 3.3.2.
-The uniform distributed stress values of on the concrete and the steel cross-sections, which represent the average stress on the two sections, are adopted as the corrected material strengths of the CFST member.
+The uniform distributed stress values on the concrete and the steel cross-sections, which represent the average stress on the two sections, are adopted as the corrected material strengths of the CFST member.
 In the following subchapters, an indirect approach is proposed to obtain the corrected material strengths of the concrete and steel sections.
@@
 	\end{itemize}
-	Based on equilibrium of axial loads and moments shown in Equation (\ref{eq-2}) and supplementary Equations (\ref{eq-3}) to (\ref{eq-5}), the confined concrete strength, $f_{cc}$, could be calculated.
+	Based on the equilibrium of axial loads and moments shown in Equation (\ref{eq-2}) and supplementary Equations (\ref{eq-3}) to (\ref{eq-5}), the confined concrete strength, $f_{cc}$, could be calculated.
 	\begin{equation}\label{eq-2}
@@
 	\par
-	Based on equilibrium of axial loads and moments shown in Equation (6) and the corresponding supplementary Equations (7) to (16), the steel bi-axial yield stress, $f_{yb}$, could be calculated as:
+	Based on the equilibrium of axial loads and moments shown in Equation (6) and the corresponding supplementary Equations (7) to (16), the steel bi-axial yield stress, $f_{yb}$, could be calculated as:
 
@@
 The original and the corrected material strengths are listed in Table \ref{tb-2}.
-It could be found that, both the concrete and the steel yield strengths are increased by the proposed correction methods, which is in line with the conclusion that the multi-axial stress states will have a positive influences on the flexural capacity of the circular CFST member.
+It could be found that both the concrete and the steel yield strengths are increased by the proposed correction methods, which is in line with the conclusion that the multi-axial stress states will have a positive influence on the flexural capacity of the circular CFST member.
 	\par
@@
 	The eight specimens are re-analysed by the DP model with the material strengths given by the correction methods.
-As discussed in Section 3.2, the correction methods has already taken the influence of concrete residual strength into consideration during correction procedure.
-Thus, the acquired confined concrete strength stays at the safe side and there is no need to consider the softening of the concrete strength for a second time.
+As discussed in Section 3.2, the correction methods have already taken the influence of concrete residual strength into consideration during correction procedure.
+Thus, the acquired confined concrete strength stays on the safe side and there is no need to consider the softening of the concrete strength for the second time.
 Therefore, the confined concrete constitution law used in DP model is defined as a perfect elasto-plastic curve.
@@
 	\par
-	Analysis of the results shown in Figure \ref{fig-9} allow concluding that the computation of material strength corrections in the DP model leads to a very good agreement the results from the 3D FE model.
+	Analysis of the results shown in Figure \ref{fig-9} allows concluding that the computation of material strength corrections in the DP model leads to a very good agreement the results from the 3D FE model.
 This is further supported by comparing the peak lateral loads, as shown in Table \ref{tb-3}.
-In the table, the maximum lateral forces of the DP models ($F_{DP}$ for the uni-axial material strengths and $F_{DP}^{Method}$ for the corrected material strengths), are compared with the value from the 3D FE model, $F_{3D}$.
+In the table, the maximum lateral forces of the DP models ($F_{DP}$ for the uniaxial material strengths and $F_{DP}^{Method}$ for the corrected material strengths), are compared with the value from the 3D FE model, $F_{3D}$.
 The ratios between the ultimate values of the 3D FE model and the DP models, $F_{DP}/F_{3D}$ and $F_{DP}^{Method}/F_{3D}$, are also shown.
@@
 3D FE model) before any other analysis.
-Although, in principle, this works for any CFST, the process itself lacks efficiency when extrapolated to a large number of members.
-Thus, the development of a material strength correction database, in the form of member property-dependent equations, is particularly relevant, since detailed modelling procedures need not be carried-out again.
-In the following sections, a comprehensive parametric study, aims at the development of such material strength correction database, is described.
+Although in principle, this works for any CFST, the process itself lacks efficiency when extrapolated to a large number of members.
+Thus, the development of a material strength correction database, in the form of member property-dependent equations, is particularly relevant, since detailed modelling procedures need not be carried out again.
+In the following sections, a comprehensive parametric study aims at the development of such material strength correction database, is described.
 The statistic procedure is taken and the material strength correction equations, which is independent on the 3D FE model, are derived.
+	\par
 	\subsection{Parametric Study}
-	To carry out the parametric study, a number of parameters that define both the properties of the CFST member and the load conditions were considered: 1) diameter-to-thickness ratio of the steel tube; 2) concrete uni-axial compressive strength; 3) steel uni-axial yield stress and 4) axial load level.
+	To carry out the parametric study, a number of parameters that define both the properties of the CFST member and the load conditions were considered: 1) diameter-to-thickness ratio of the steel tube; 2) concrete uniaxial compressive strength; 3) steel uniaxial yield stress and 4) axial load level.
 As shown in Table \ref{tb-4}, eleven steel tubes were adopted, between high and moderate values of diameter-to-thickness ratio.
@@
 	\par
-	The axial load level will play an important role to the corrected material strength, as the increase of the axial load will result in the change of location of the neutral axis.
+	The axial load level will play an important role in the corrected material strength, as the increase of the axial load will result in the change of location of the neutral axis.
 Thus, five different axial load levels, $μ_n$, are adopted, namely 0\% (no axial load), 5\%, 10\%, 20\% and 30\%.
@@
 	\par
-	By combining the 88 CFST columns with the 5 axial load levels, 440 monotonic flexural analysis were conducted.
+	By combining the 88 CFST columns with the 5 axial load levels, 440 monotonic flexural analysis was conducted.
 Each of the columns was laterally loaded up to a drift ratio level of 7\%.
@@
 	In order to represent the wide set of members with a single representative parameter, a section factor, $ξ$, is adopted, as shown in Equation (18).
-In a simplified manner, the section factor consists the cross-section slenderness, $D/t$, unconfined concrete strength, $f_c$, and uni-axial steel yield stress $f_y$.
+In a simplified manner, the section factor consists the cross-section slenderness, $D/t$, unconfined concrete strength, $f_c$, and uniaxial steel yield stress $f_y$.
 For CFST members with given concrete and steel types, the larger values of $ξ$ indicate a stronger concrete core and a weaker steel tube, and vice versa.
@@
 	Regarding the strength corrections of the concrete core, the ratio between the confined and plain strength values, $f_{cc}/f_c$, are plotted against section factor $ξ$ in Figure \ref{fig-10}.
-The scatters of the CFST members are grouped according to the axial load levels ,$μ_n$, and are classified in different colours.
+The scatters of the CFST members are grouped according to the axial load levels, $μ_n$, and are classified in different colours.
 Analysis of the results allows concluding that regardless of the axial load level, the values of $f_{cc}/f_c$ were consistently larger than 1.0.
@@
 	\par
-	It could also be found that, the scatter distributions of different axial load levels trended to be similar.
+	It could also be found that the scatter distributions of different axial load levels tended to be similar.
 This indicates that the confinement effect of the concrete core does not depend on the axial load level, for flexural loading scenarios.
@@
 2005 \cite{RN29}, for CFST members under centrally compression and flexural force, the confined strength of the concrete core should be different.
-Thus, the proposed confined concrete strength equation only applies to the case that the circular CFST column is under bending combined with constant axial load.
+Thus, the proposed confined concrete strength equation only applies to the case that the circular CFST column is under bending combined with a constant axial load.
 	\subsection{Strength Correction Equations for Steel}
-	Similar to the corrections of the concrete, the ratio between the steel bi-axial yield stress and uni-axial yield stress, $f_{yb}/f_y$, are plotted against $ξ$ in Figure \ref{fig-11} for each $μ_n$.
+	Similar to the corrections of the concrete, the ratio between the steel bi-axial yield stress and uniaxial yield stress, $f_{yb}/f_y$, are plotted against $ξ$ in Figure \ref{fig-11} for each $μ_n$.
 Analysis of the results shown in $f_{yb}/f_y$ allows concluding that similarly to the values for concrete, regardless of the axial load level, the values of fyb/fy were always larger than 1.0.
@@
 The $c_s$ values, which will make about 84\% of the scatters above the strength equation line of each axial load level, are listed in Table \ref{tb-5}.
-The main purpose of introduce the parameter $c_s$ is to reduce the possibility of overestimating the steel bi-axial stress and thus, make the material correction equation stay at the safe side.
+The main purpose of introducing the parameter $c_s$ is to reduce the possibility of overestimating the steel bi-axial stress and thus, make the material correction equation stay on the safe side.
 	\par
@@
 	The obtained lateral force-drift ratio curves of the eight specimens are shown in Figure \ref{fig-12}.
-For each member, the numerical results of the DP model with both the uni-axial and corrected material properties (labelled with $FE_{DP}$ and $FE_{DP}^{Eq}$, respectively) are plotted against the results of the experimental tests.
-Analysis of the results shown in Figure \ref{fig-12} allow concluding that the computation of DP model (with the use of the material strength correction equations) leads to a good agreement against the experimental results.
-In general, there is an increase of the bending capacity of the CFST member when the material strength correction is considered, compared with the DP model with the uni-axial properties.
+For each member, the numerical results of the DP model with both the uniaxial and corrected material properties (labelled with $FE_{DP}$ and $FE_{DP}^{Eq}$, respectively) are plotted against the results of the experimental tests.
+Analysis of the results shown in Figure \ref{fig-12} allows concluding that the computation of DP model (with the use of the material strength correction equations) leads to a good agreement against the experimental results.
+In general, there is an increase of the bending capacity of the CFST member when the material strength correction is considered, compared with the DP model with the uniaxial properties.
 In terms of accuracy, the DP model with corrected strength fits better with the experimental data, especially in the post-yield stage.
@@
 	\par
-	The benefits of applying the material strength correction equations is further supported by comparing the peak test and numerical lateral loads, as shown in Table \ref{tb-7}.
+	The benefits of applying the material strength correction equations are further supported by comparing the peak test and numerical lateral loads, as shown in Table \ref{tb-7}.
 In the table, the maximum lateral forces of the DP models, $F_{DP}$ for the uncorrected material strengths and $F_{DP}^{Eq}$ for the corrected material strengths with the use of regression equations, are compared with the values from experimental tests, $F_{test}$.
@@
 The results obtained are shown in Table \ref{tb-8}.
-Analysis of the results shown in Table \ref{tb-8} allow concluding that by computing the corrected material strengths into the design methodology of Eurocode 4, the average differences between the code and the experimental evidence reduce from 24\% to 15\%.
+Analysis of the results shown in Table \ref{tb-8} allows concluding that by computing the corrected material strengths into the design methodology of Eurocode 4, the average differences between the code and the experimental evidence reduce from 24\% to 15\%.
 The design values of all specimens are still lower than the test results, which indicates that this methodology is still on the conservative side.
@@
 	\section{Conclusions}
-	This research paper has described the development of multi-axial stress states, namely the concrete confinement effects and steel bi-axial stress state, which were existing in CFST member.
-The influence of the multi-axial stress states on the bending capacity of circular CFST member had been verified via experimental and numerical studies.
-Based on the 3D FE model, material strength correction methods were developed.
-By conducting a parametric study consisting of 440 CFST members under flexural loading, combined with different levels of axial load, section factor-dependent material strength correction equations were derived.
+	This research paper has detailed the methodologies and the equations proposed for flexural loaded circular CFST columns, which aim to consider the material strength variance under multi-axial stress states.
+The influence of the multi-axial stress states, namely the concrete confinement effect and the steel bi-axial stress state, on the bending capacity of circular CFST member had been discussed.
+Material strength correction methods, which can acquire the confined concrete strength and steel bi-axial stress from the 3D FE model prediction, were devised and calibrated.
+A parametric study, which consisted of 440 CFST members under flexural loading, combined with different levels of axial load, were carried out.
+Given the results of the parametric study, $ξ$ and $μ_n$ dependent material strength correction equations were derived to account for the development of multi-axial stress states on both parts of circular CFST members under flexural force.
 Within the scope of the results obtained, the following conclusions can be withdrawn:
 	\begin{itemize}
-		\item The development of multi-axial stress states in circular CFST members may significantly enhance the flexural strength of the members.
-This is somehow neglected with the current design guidelines of Eurocode 4, given that the code only accounts for the development of confinement and not the bi-axial stress state of the steel tube walls;
+		\item Not only the concrete confinement effect but also the steel bi-axial stress state are discovered to have a positive influence on the bending capacity of circular CFST members.
+By validating against the experimental results, the previously developed strength correction methods are proved to be inaccurate to consider the influence of the axial load on the multi-axial stress states;
 
-		\item In order to overcome the limitations of the DP model, a material strength correction method, which basically produces the ratio of required increase of the uniaxial material properties, is devised and calibrated against the results of the detailed 3D FE model.
-The approach proved to improve the accuracy of the DP model;
+		\item By validating against the results of the 3D FE model, the proposed material strength correction methods are verified to improve the accuracy of the DP model on the flexural behaviour prediction of circular CFST members;
 
-		\item Based on the parameteric study, it is found that the confined concrete strength can be considered to be independent from the axial load level, for cases that the circular CFST members are under flexural forces and the constant axial load level is less than 30\%.
+		\item Based on the parametric study, it is observed that the confined concrete strength can be considered to be independent of the axial load level, for cases that the circular CFST members are under flexural forces and the constant axial load level is less than 30\%;
 
-		\item The development of confinement on the concrete core decreases as the proposed section factor, $ξ$, increases.
+		\item The development of confinement on the concrete core decreases as the proposed section factor, $ξ$, increases;
 
@@
 
-		\item Given the results of the parametric study, $ξ$ and $μ_n$ dependent material strength correction equations were derived to account for the development of multi-axial stress states on both parts of circular CFST members under flexural force.
-
-		\item Both proposed material correction equations were validated against experimental evidence, and found to provide improve the accuracy of both simplified modelling and design procedures.
-By comparing with the experimental tests shown in the paper, the average differences between the peak flexural capacities of the test specimens and the distributed plasticity model decrease from 11\% to 1\%, without and with the application of the proposed material strength correction equations, respectively.
-Moreover, computing the corrected material strengths in the design methodology of EC4 leads to a reduction in the average differences between the code and the experimental evidence from 24\% to 15\%, without and with the application of the proposed material strength correction equations, respectively.
+		\item The proposed material correction equations are validated against experimental evidence and found to improve the accuracy of both simplified modelling and Eurocode 4 design procedures.
 	\end{itemize}

### 2018-03-28 Paper7.tex
$(data)

@@
 As concluded from previous experimental studies (Silva et al.
-2016 \cite{Silva2016} and Silva et al.
-2017 \cite{RN140}), The concrete core constrains the steel tube to its interior, thus delaying the occurrence of the local buckling to higher levels of deformation and the ductility of the steel tube is improved.
+2016 \cite{Silva2016}, Silva et al.
+2017 \cite{RN140} and Duarte et al.
+\cite{DUARTE2016274}), the concrete core constrains the steel tube to its interior, thus delaying the occurrence of the local buckling to higher levels of deformation and the ductility of the steel tube is improved.
 Besides its excellent ductility, the composition of concrete and steel will also cause the two components under multi-axial stress state and thus, lead to the material properties variance.

### 2018-03-28 Paper7.tex
$(data)

@@
 \title{Assessment of Multi-Axial Stress State effects of Circular Concrete-Filled Steel Tubular Columns under Flexural Loading}
-\author{Yadong Jiang \and António Silva \and Bledar Kalemia \and José Miguel Castro \and Ricardo Monteiro}
+\author{Yadong Jiang \and António Silva \and Bledar Kalemia \and José Miguel Castro \and Ricardo Monteiro \and Nuno Silvestre}
 
@@
 
-	\section{Multi-axial Stress States of Circular CFST Members}
+	\section{Influence of Multi-axial Stress States}
 	\subsection{Multi-axial Stress States}
@@
 	\par
-	\subsection{Previous Studies on Multi-axial Stress State Influence}
+	\subsection{Previous Studies on Multi-axial Stress State}
 	In the past, there were many researchers had carried out the studies on the prediction of confined concrete strength for CFST members (Han et al.
@@
 But regarding the specimens with constant axial loads (plots on the right column), nearly no improvement of the DP model results is found by applying the correction methods, by comparing its results with the original DP model predictions.
-As constant factors were used to correct the steel stress in the correction methods given by the two research works, it could be summarized that the steel bi-axial stress state has a relationship with the axial load level.
+As constant factors were used to correct the steel stress in the correction methods given by the two research works, it could be summarized that the steel bi-axial stress state has a relationship with the axial load level, which is not considered in the aforementioned correction methods.
 	\par
@@
 
-	\subsection{Yield Points of the Concrete and Steel Sections}
+	\subsection{Yield Points of Concrete and Steel Sections}
 	The yield moments of the concrete core and the steel tube are directly related to their material strengths, namely the confined concrete strength and the steel bi-axial yield stress.
@@
 For CFST members with given concrete and steel types, the larger values of $ξ$ indicate a stronger concrete core and a weaker steel tube, and vice versa.
-	\subsection{Strength Correction Equations for Concrete}
+	\subsection{Strength Correction Equation for Concrete}
 	Regarding the strength corrections of the concrete core, the ratio between the confined and plain strength values, $f_{cc}/f_c$, are plotted against section factor $ξ$ in Figure \ref{fig-10}.
@@
 Thus, the proposed confined concrete strength equation only applies to the case that the circular CFST column is under bending combined with a constant axial load.
-	\subsection{Strength Correction Equations for Steel}
+	\subsection{Strength Correction Equation for Steel}
 	Similar to the corrections of the concrete, the ratio between the steel bi-axial yield stress and uniaxial yield stress, $f_{yb}/f_y$, are plotted against $ξ$ in Figure \ref{fig-11} for each $μ_n$.
